---
title: "R Notebook"
author: "David John"
output:
  html_document:
    df_print: paged
---

#1.) Import Data
## 1.1) Import packages
```{r message=FALSE}
#load libraries
library(dplyr)
library(ggpubr)

require(scales)

#import scImpute
#install.packages("devtools")
#library(devtools)
#install_github("Vivianstats/scImpute")
library(scImpute)
library(Seurat)
source("Import10X-HelperFunctions.R")
```
---

##Import Ref Genome and Gene Biotypes
```{r}
#only lncRNAs
library(refGenome)
setwd("/media/ATLAS_Genomes_Annotations/mouse/GRCm38");
ens <- ensemblGenome()
read.gtf(ens, "Mus_musculus.GRCm38.81.gtf")
my_gene <- getGenePositions(ens);rownames(my_gene)<-my_gene$gene_id
biotypes<-data.frame(geneName=my_gene$gene_name, biotype=my_gene$gene_biotype )
```



## 1.2) Load Data and assign condition
```{r Import, message=FALSE}
###############################################################
### 1.)           Import and filter Data                   ####
###############################################################
setwd("/home/david/PowerFolders/Arbeit/2018/Conferences/Keystone2019/rData/")


#Static Parameters
Path.WholeHeart <- c("/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/Young1",
                "/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/Young2",
                "/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/Young3",
                "/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/Old1",
                "/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/Old2",
                "/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/Old3")
SAMPLENAMES_WholeHeart <- c("Young1","Young2","Young3","Old1","Old2","Old3")


#NUCLEAR_MATRIX <- read.table("/media/ATLAS_NGS_storage/Stefanie/singleCell_Berlin/mouse-heart-ercc-tpm.txt/mouse-heart-ercc-tpm.txt")
WholeHeart <- combineSeuratObjectsCCA(pathways = Path.WholeHeart, ids = SAMPLENAMES_WholeHeart)

mito.genes <- grep(pattern = "^mt-", x = rownames(x = WholeHeart@data), value = TRUE)
percent.mito <- Matrix::colSums(WholeHeart@raw.data[mito.genes, ])/Matrix::colSums(WholeHeart@raw.data)
WholeHeart <- AddMetaData(object = WholeHeart, metadata = percent.mito, col.name = "percent.mito")
WholeHeart <- AddMetaData(object = WholeHeart, metadata = WholeHeart@ident, col.name = "orig.ident")

condition <- c()
for (barcode in colnames(WholeHeart@data)){
  if (startsWith(barcode,"Old")) { condition<-c(condition,"Old")}
  else if (startsWith(barcode,"Young")) { condition<-c(condition,"Young")}
  else {print("unexpected condition")}
}
names(condition)<-WholeHeart@cell.names
WholeHeart <- AddMetaData(object = WholeHeart, metadata = condition, col.name = "condition");rm(condition)

WholeHeart <- FilterCells(object = WholeHeart, subset.names = c("nGene", "percent.mito"), low.thresholds = c(1000, -Inf), high.thresholds = c(Inf, 0.2))

```


## 1.2) Impute the dataset with scImpute
Run only once, as the files are stored on the Hard drive
```{r message=FALSE, warning=FALSE}
# library(scImpute)
# library(Seurat)
# 
# imputeData <- function(pathway,id, cluster=12, ncores=20, drop_thre=0.5){
#   path.Matrix<-paste(pathway,"Matrix.csv",sep="/")
#   path.Imputed.Matrix <- paste(pathway, "scImpute", id, sep="/")
#   Ten_X <- Read10X(pathway)
#   write.csv(as.data.frame(as.matrix(Ten_X)), file = path.Matrix)
#   scimpute(count_path = path.Matrix, 
#            out_dir = path.Imputed.Matrix, Kcluster = cluster, ncores=ncores, drop_thre = drop_thre)
# }
# 
# imputeData("/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/Young1", "young1")
# imputeData("/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/Young2", "young2")
# imputeData("/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/Young3", "young3")
# 
# imputeData("/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/Old1", "old1")
# imputeData("/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/Old2", "old2")
# imputeData("/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/Old3", "old3")

```

## 1.3) Load imputed dataset
```{r LoadImpute, message=FALSE}
#SAMPLENAMES_WholeHeart <- c("young1","young2","young3","old1","old2","old3")
#WholeHeart.Imputed <- combineScImputedSeuratObjectsCCA(pathways = Path.WholeHeart, ids = SAMPLENAMES_WholeHeart)
#saveRDS(WholeHeart.Imputed, file = "/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/WholeHeart.Imputed.rds")
WholeHeart.Imputed<-readRDS("/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/WholeHeart.Imputed.rds")

mito.genes <- grep(pattern = "^mt-", x = rownames(x = WholeHeart.Imputed@data), value = TRUE)
percent.mito <- Matrix::colSums(WholeHeart.Imputed@raw.data[mito.genes, ])/Matrix::colSums(WholeHeart.Imputed@raw.data)
WholeHeart.Imputed <- AddMetaData(object = WholeHeart.Imputed, metadata = percent.mito, col.name = "percent.mito")
WholeHeart.Imputed <- AddMetaData(object = WholeHeart.Imputed, metadata = WholeHeart.Imputed@ident, col.name = "orig.ident")

condition <- c()
for (barcode in colnames(WholeHeart.Imputed@data)){
  if (startsWith(barcode,"old")) { condition<-c(condition,"Old")}
  else if (startsWith(barcode,"young")) { condition<-c(condition,"Young")}
  else {print("unexpected condition")}
}
names(condition)<-WholeHeart.Imputed@cell.names
WholeHeart.Imputed <- AddMetaData(object = WholeHeart.Imputed, metadata = condition, col.name = "condition");rm(condition)

WholeHeart.Imputed <- FilterCells(object = WholeHeart.Imputed, subset.names = c("nGene", "percent.mito"), low.thresholds = c(1000, -Inf), high.thresholds = c(Inf, 0.2))

```

# 2.) Quality Control
## 2.1) Number of UMI's and mT content
```{r QCStats}
par(mfrow = c(2, 2))
GenePlot(object = WholeHeart, gene1 = "nUMI", gene2 = "percent.mito",)
GenePlot(object = WholeHeart, gene1 = "nUMI", gene2 = "nGene")
GenePlot(object = WholeHeart.Imputed, gene1 = "nUMI", gene2 = "percent.mito", sub="imputed")
GenePlot(object = WholeHeart.Imputed, gene1 = "nUMI", gene2 = "nGene", sub="imputed")
```

##2.2) Run clustering
```{r Clustering}
WholeHeart <- RunPCA(object = WholeHeart, pc.genes = WholeHeart@var.genes, do.print = TRUE, pcs.print = 1:5, genes.print = 5)
WholeHeart<-ProjectPCA(object = WholeHeart, do.print = FALSE)
PCHeatmap(object = WholeHeart, pc.use = 1:12, cells.use = 500, do.balanced = TRUE, label.columns = FALSE, use.full = FALSE)
WholeHeart <- FindClusters(object = WholeHeart, reduction.type = "pca", dims.use = 1:5, resolution = 0.6, print.output = 0, save.SNN = TRUE)
PrintFindClustersParams(object = WholeHeart)
WholeHeart <- RunTSNE(object = WholeHeart, dims.use = 1:5, do.fast = TRUE)

WholeHeart.Imputed <- RunPCA(object = WholeHeart.Imputed, pc.genes = WholeHeart.Imputed@var.genes, do.print = TRUE, pcs.print = 1:5, genes.print = 5)
WholeHeart.Imputed<-ProjectPCA(object = WholeHeart.Imputed, do.print = FALSE)
PCHeatmap(object = WholeHeart.Imputed, pc.use = 1:12, cells.use = 500, do.balanced = TRUE, label.columns = FALSE, use.full = FALSE)
WholeHeart.Imputed <- FindClusters(object = WholeHeart.Imputed, reduction.type = "pca", dims.use = 1:5, resolution = 0.6, print.output = 0, save.SNN = TRUE)
PrintFindClustersParams(object = WholeHeart.Imputed)
WholeHeart.Imputed <- RunTSNE(object = WholeHeart.Imputed, dims.use = 1:5, do.fast = TRUE)
```

# 3.) Results
## 3.1.) Clusters
### 3.1.1.) TSNE and FeaturePlots
```{r TSNE}
TSNEPlot(object = WholeHeart, label=T, pt.size = 1.1, do.return=TRUE,plot.title="Not Imputed")
TSNEPlot(object = WholeHeart.Imputed, label=T, pt.size = 1.1, do.return=TRUE, plot.title="scImpute")
DimPlot(object = WholeHeart.Imputed, reduction = "cca")
rm(a)
a<-FeaturePlot(object = WholeHeart, features.plot = c("Cdh5","Pecam1"), cols.use = c("grey", "blue"), pt.size = 1, do.return=TRUE)
a<-ggarrange(a$Cdh5,a$Pecam1);annotate_figure(a, top = text_grob("Raw", color = "red", face = "bold", size = 16),)

a<-FeaturePlot(object = WholeHeart.Imputed, features.plot = c("Cdh5","Pecam1"), cols.use = c("grey", "blue"), pt.size = 1, do.return=TRUE, vector.friendly = TRUE)
a<-ggarrange(a$Cdh5,a$Pecam1);annotate_figure(a, top = text_grob("Imputed", color = "red", face = "bold", size = 16),)
```


```{r}
WholeHeart<-SetAllIdent(WholeHeart,id="res.06")
TSNEPlot(object = WholeHeart, label=T, do.label = T, label.size = 9, pt.size = 0.5, do.return=TRUE,plot.title="Not Imputed")
VlnPlot(object = WholeHeart, features.plot = c("Cyyr1"))


WholeHeart<-SetAllIdent(WholeHeart,id="condition")
TSNEPlot(object = WholeHeart, label=T, pt.size = 0.5, do.return=TRUE,plot.title="Not Imputed")

WholeHeart<-SetAllIdent(WholeHeart,id="orig.ident")
TSNEPlot(object = WholeHeart, label=T, pt.size = 0.5, do.return=TRUE,plot.title="Not Imputed")


WholeHeart.Imputed<-SetAllIdent(WholeHeart.Imputed,id="orig.ident")
TSNEPlot(object = WholeHeart.Imputed, label=T, pt.size = 0.5, do.return=TRUE, plot.title="scImpute")
```


### 3.1.2.) Cluster Specific Markers Markers
```{r message=FALSE, warning=FALSE}
WholeHeart.Markers <- FindAllMarkers(object = WholeHeart, only.pos = TRUE, min.pct = 0.25, thresh.use = 0.25, min.diff.pct = 0.25)
WholeHeart.Imputed.Markers <- FindAllMarkers(object = WholeHeart.Imputed, only.pos = TRUE, min.pct = 0.25, min.diff.pct = 0.25)

```

##### Top 10 Markers (Raw)
```{r}
top.Markers.WholeHeart <- WholeHeart.Markers %>% group_by(cluster) %>% top_n(10, avg_logFC)
top.Markers.WholeHeart
```


##### Top 10 Markers (Imputed)
######The clusters seem to be much more stringent and also lower expressed genes are now present at higher levels and more cluster specific
```{r}
top.Markers.WholeHeart.Imputed <- WholeHeart.Imputed.Markers %>% group_by(cluster) %>% top_n(10, avg_logFC)
write.csv(top.Markers.WholeHeart.Imputed,file = "/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/NewAnalysis22.11.18/Imputed/Top10MarkerGenesPerCluster.csv")
top.Markers.WholeHeart.Imputed
```

### 3.1.3.) FeaturePlots of Cluster Specific Markers 
##### Raw

```{r}
a<-FeaturePlot(object = WholeHeart, features.plot = c("Fabp4","Vwf","Cd74","Myh6","Pecam1","Cdh5", "Lyz2", "Fbn1"),do.return=T, cols.use = c("grey", "blue"), reduction.use = "tsne", vector.friendly = TRUE, pt.size = 1.5)
annotate_figure(ggarrange(a$Fabp4,a$Vwf,a$Cd74,a$Myh6), top = text_grob("Raw", color = "red", face = "bold", size = 16),)
annotate_figure(ggarrange(a$Pecam1,a$Cdh5,a$Lyz2,a$Fbn1), top = text_grob("Raw", color = "red", face = "bold", size = 16),)

VlnPlot(object = WholeHeart.Imputed, features.plot = c("Myh6","Cdh2","Ttn","Fbn1","Lyz2","Pln","Cdh5","Pecam1","Wdr17","Cyyr1","Bicc1","Pck1","F13a1"), group.by = "res.0.6")
#a<-FeaturePlot(object = WholeHeart.Imputed, features.plot = top.Markers.WholeHeart$gene,do.return=T, cols.use = c("grey", "blue"), reduction.use = "tsne", vector.friendly = TRUE)

```
##### Imputed

```{r}
a<-FeaturePlot(object = WholeHeart.Imputed, features.plot = c("Fabp4","Vwf","Cd74","Myh6","Pecam1","Cdh5", "Lyz2", "Fbn1"),do.return=T, cols.use = c("grey", "blue"), reduction.use = "tsne", vector.friendly = TRUE, , pt.size = 1.5)
annotate_figure(ggarrange(a$Fabp4,a$Vwf,a$Myh6,a$Pecam1), top = text_grob("Imputed", color = "red", face = "bold", size = 16),)
annotate_figure(ggarrange(a$Pecam1,a$Cdh5,a$Lyz2,a$Fbn1), top = text_grob("Imputed", color = "red", face = "bold", size = 16),)
```

### 3.1.4.) ViolinPlots of Cluster Specific Markers
#### Raw
```{r}
a<-VlnPlot(object = WholeHeart, features.plot = c("Fabp4","Myh6",       "Cd74","Myh6","Pecam1","Cdh5", "Lyz2", "Fbn1"),return.plotlist = TRUE, do.return=TRUE)
annotate_figure(ggarrange(a[[1]],a[[2]],a[[3]],a[[4]]), top = text_grob("Raw", color = "red", face = "bold", size = 16))
annotate_figure(ggarrange(a[[5]],a[[6]],a[[7]],a[[8]]), top = text_grob("Raw", color = "red", face = "bold", size = 16))

```

####Imputed
```{r fig.width=15}
a<-VlnPlot(object = WholeHeart.Imputed, features.plot = c("Fabp4","Vwf","Cd74","Myh6","Pecam1","Cdh5", "Lyz2", "Fbn1"),return.plotlist = TRUE, do.return=TRUE)
annotate_figure(ggarrange(a[[1]],a[[2]],a[[3]],a[[4]]), top = text_grob("Impute", color = "red", face = "bold", size = 16),)
annotate_figure(ggarrange(a[[5]],a[[6]],a[[7]],a[[8]]), top = text_grob("Impute", color = "red", face = "bold", size = 16),)


```
Cluster belonging to which cell Type:
Endothelial Cells: 5,6,7,12




### 3.1.5 Age regulated lncRNAS
#RAW
```{r}
WholeHeart <- SetAllIdent(object = WholeHeart, id = "condition")
WholeHeart.YoungvsOld <- FindMarkers(object = WholeHeart, ident.1 = c("Young"),ident.2 = c("Old"), only.pos = FALSE, min.pct = 0, thresh.use = 0.25)
df1<-data.frame(geneName=my_gene$gene_name,biotype=my_gene$gene_biotype)
df2<-data.frame(geneName=rownames(WholeHeart.YoungvsOld),WholeHeart.YoungvsOld)
df<-merge(df1,df2,by = "geneName");df_linc<-df[df$biotype!="protein_coding",]
WholeHeart.YoungUp<-as.character(df_linc[df_linc$avg_logFC>0  & df_linc$p_val_adj<0.05,"geneName"]);cat(CM_youngUp,sep = ",")
WholeHeart.OldUp<-as.character(df_linc[df_linc$avg_logFC<0  & df_linc$p_val_adj<0.05,"geneName"]);cat(CM_OldUp,sep = ".")

WholeHeart.YoungUp<-as.character(df_linc[df_linc$avg_logFC>0,"geneName"]);cat(CM_youngUp,sep = "\n")
WholeHeart.OldUp<-as.character(df_linc[df_linc$avg_logFC<0,"geneName"]);cat(CM_OldUp,sep = "\n")

```
---
###Save and reload everithing here
```{r}
save.image("/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/NewAnalysis22.11.18/ImputedDataset.David.28.02.19.RData")
load("/media/ATLAS_NGS_storage/Julian-Wagner/scRNA-Seq_Mouse_RamonBerlin_/HeartData/NewAnalysis22.11.18/ImputedDataset.David.28.02.19.RData")
```
---


## 3.2.) Subset of Specific Cell Types
####combine cluster with age information
#####Raw

```{r}
cluster_condition <- c()
for (i in 1:length(WholeHeart@data[1,])){
  add<-paste(WholeHeart@meta.data$res.0.6[i],"-",WholeHeart@meta.data$condition[i],sep = "")
  cluster_condition<-c(cluster_condition,add)
}
names(cluster_condition)<-WholeHeart@cell.names
WholeHeart@meta.data$cluster_condition <- cluster_condition
rm(cluster_condition)
```

#####Imputed
```{r}
cluster_condition <- c()
for (i in 1:length(WholeHeart.Imputed@data[1,])){
  add<-paste(WholeHeart.Imputed@meta.data$res.0.6[i],"-",WholeHeart.Imputed@meta.data$condition[i],sep = "")
  cluster_condition<-c(cluster_condition,add)
}
names(cluster_condition)<-WholeHeart.Imputed@cell.names
WholeHeart.Imputed@meta.data$cluster_condition <- cluster_condition
rm(cluster_condition)
```



## rename Clusters
#### Raw
```{r}
WholeHeart <- SetAllIdent(WholeHeart,id="res.0.6")
VlnPlot(object = WholeHeart, features.plot = c("Ttn","Pcdh9", "Fabp4"),x.lab.rot = T, size.x.use = 7) 

#rename all clusters

clusterNames <- c("Cardiomyocytes", "Cardiomyocytes2","Cardiomyocytes2", "Fibroblasts","Endothelial_Cells", "Endothelial_Cells"
                  , "Endothelial_Cells", "Endothelial_Cells","Endothelial_Cells", "Unknown0", 
                   "Unknown1", "Unknown2", "Unknown3", "Unknown4", "Unknown5", "Unknown6", "Unknown7", "Unknown8")


length(table(wholeHeartYoungOld@ident))
length(WholeHeart)

for (i in 0:length(table(wholeHeartYoungOld@ident))){
  wholeHeartYoungOld<-RenameIdent(object = wholeHeartYoungOld, old.ident.name = i, new.ident.name = clusterNames[i+1])
}
```


#### Imputed
```{r}
VlnPlot(object = WholeHeart.Imputed, features.plot = c("Ttn","Pcdh9", "Fabp4"),x.lab.rot = T, size.x.use = 7) 

WholeHeart.Imputed<-SetAllIdent(WholeHeart.Imputed,id = "res.0.6")

clusterNames <- c("Cardiomyocytes", "Endothelial Cells","Endothelial Cells2",
                  "Cardiomyocytes2","Unknown4","Unknown5","Fibroblasts","Fibroblasts",
                  "Unknown8","Unknown9","Unknown10","Unknown11","Unknown12","Unknown13",
                  "Unknown14","Unknown15","Unknown16","Unknown17","Unknown18","Unknown19")
length(table(WholeHeart.Imputed@ident))
length(clusterNames)


for (i in 1:length(table(WholeHeart.Imputed@ident))-1){
  cat(i,clusterNames[i+1],"\n")
  WholeHeart.Imputed<-RenameIdent(object = WholeHeart.Imputed, old.ident.name = i, new.ident.name = clusterNames[i+1])
}
WholeHeart.Imputed<-AddMetaData(WholeHeart.Imputed, metadata = WholeHeart.Imputed@ident, col.name = "clusterNames")
table(WholeHeart.Imputed@ident)
table(clusterNames)
```

```{r}
VlnPlot(object = WholeHeart, features.plot = c("Myh6","Fabp4", "Pcdh9"))
VlnPlot(object = WholeHeart.Imputed, features.plot = c("Myh6","Fabp4", "Pcdh9"))

```


### 3.2.1.) Endthelial Cells
##### Raw
```{r}
#Extract Cardiomyocytes
endothelialCells <- SubsetData(object = WholeHeart, ident.use = c("Endothelial Cells","Endothelial Cells"))
endothelialCells <- SetAllIdent(object = endothelialCells, id = "condition")
endothelialCells_regulated_old_young <- FindMarkers(endothelialCells, ident.1 = "Old", ident.2 = "Young", only.pos = FALSE,print.bar = T)

endothelialCells_regulated_old_young <- endothelialCells_regulated_old_young[order(endothelialCells_regulated_old_young$avg_logFC),]
endothelialCells_regulated_old_young <- endothelialCells_regulated_old_young[order(cardiomyocytes_regulated_old_young$p_val),]
topRegulated<- rbind(head(endothelialCells_regulated_old_young),tail(endothelialCells_regulated_old_young))
VlnPlot(object = endothelialCells, features.plot = c(rownames(topRegulated)))

VlnPlot(object = wholeHeartYoungOld, features.plot = c(rownames(head(cardiomyocytes_regulated_old_young))))
VlnPlot(object = wholeHeartYoungOld, features.plot = c("Plvap"))

```

##### Imputed
```{r}
#Extract Cardiomyocytes
endothelialCells.Imputed <- SubsetData(object = WholeHeart.Imputed, ident.use = c("Cardiomyocytes","Cardiomyocytes2"))
endothelialCells.Imputed <- SetAllIdent(object = endothelialCells.Imputed, id = "condition")
endothelialCells_regulated_old_young.Imputed <- FindMarkers(endothelialCells.Imputed, ident.1 = "Old", ident.2 = "Young", only.pos = FALSE,print.bar = T)

endothelialCells_regulated_old_young.Imputed <- endothelialCells_regulated_old_young.Imputed[order(endothelialCells_regulated_old_young.Imputed$avg_logFC),]
endothelialCells_regulated_old_young.Imputed <- endothelialCells_regulated_old_young.Imputed[order(endothelialCells_regulated_old_young.Imputed$p_val),]
topRegulated<- rbind(head(endothelialCells_regulated_old_young.Imputed),tail(endothelialCells_regulated_old_young.Imputed))
VlnPlot(object = endothelialCells.Imputed, features.plot = c(rownames(topRegulated)))

VlnPlot(object = wholeHeartYoungOld, features.plot = c(rownames(head(endothelialCells_regulated_old_young.Imputed))))
VlnPlot(object = wholeHeartYoungOld, features.plot = c("Plvap"))

```


---
### 3.2.1.) Cardiomyocytes
##### Raw
```{r}

```
---
##### Imputed
```{r}
#Extract Cardiomyocytes
WholeHeart.Imputed<-SetAllIdent(WholeHeart.Imputed,id = "clusterNames")
table(WholeHeart.Imputed@ident)
cardiomyocytes <- SubsetData(object = WholeHeart.Imputed, ident.use = c("Cardiomyocytes","Cardiomyocytes2"))
cardiomyocytes <- SetAllIdent(object = cardiomyocytes, id = "condition")
cardiomyocytes_regulated_old_young <- FindMarkers(cardiomyocytes, ident.1 = "Old", ident.2 = "Young", only.pos = FALSE,print.bar = T)

cardiomyocytes_regulated_old_young <- cardiomyocytes_regulated_old_young[order(cardiomyocytes_regulated_old_young$avg_logFC),]
cardiomyocytes_regulated_old_young <- cardiomyocytes_regulated_old_young[order(cardiomyocytes_regulated_old_young$p_val),]
topRegulated<- rbind(head(cardiomyocytes_regulated_old_young),tail(cardiomyocytes_regulated_old_young))
VlnPlot(object = cardiomyocytes, features.plot = c(rownames(topRegulated)))

VlnPlot(object = wholeHeartYoungOld, features.plot = c(rownames(head(cardiomyocytes_regulated_old_young))))
VlnPlot(object = wholeHeartYoungOld, features.plot = c("Plvap"))

```

```{r}
#cluster Cardiomyocytes
cardiomyocytes <- RunCCA(object = cardiomyocytes, group1 = WhichCells(object = cardiomyocytes, ident = "Old"), group2 = WhichCells(object = cardiomyocytes, ident = "Young"),)
cardiomyocytes <- AlignSubspace(object = cardiomyocytes, reduction.type = "cca", grouping.var = "condition", dims.align = 1:20)
cardiomyocytes <- RunTSNE(object = cardiomyocytes, dims.use = 1:10, do.fast = TRUE, reduction.use = "cca")
cardiomyocytes <- FindClusters(object = cardiomyocytes, reduction.type = "cca", dims.use = 1:10, save.SNN = TRUE, force.recalc=TRUE)
cardiomyocytes <- AddMetaData(object = cardiomyocytes, metadata = cardiomyocytes@ident, col.name = "ccaClustersCardiomyocytes")

TSNEPlot(object = cardiomyocytes, label=T, pt.size = 0.6)
TSNEPlot(object = cardiomyocytes, label=T, pt.size = 0.6, group.by = "condition")


#Find Clusterspcific genes
cardiomyocytes <- SetAllIdent(object = cardiomyocytes, id = "ccaClusters")
cardiomyocytes.Cluster_markers <- FindAllMarkers(object = cardiomyocytes,, min.pct = 0.25, thresh.use = 0.25)
VlnPlot(object = cardiomyocytes, features.plot = c("Cdh5","Gm13601","Gm12381","Scn3a","Ccdc79","Gm13481","Fgr"))
cardiomyocytes.top10 <- wholHeeartYoungOld.markers %>% group_by(cluster) %>% top_n(10, avg_logFC)

cardiomyocytes <- SetAllIdent(object = cardiomyocytes, id = "ccaClusters")
```


---
### 3.2.1.) Fibroblats
##### Raw
```{r}

```
---
##### Imputed
```{r}

```


## 3.2.) Examine differentially expressed lncRNAs Young vs Old for different Cell Types


