---
  title: "HFpEF Models Sebastian Badder 2nd Runs (Seurat3)"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---
  
# Import packages
```{r message=FALSE}
#load libraries
library(dplyr)
library(ggpubr)
library(reshape2)
require(scales)
library(ggplot2)


source("/home/david/scRNA-SEQ-ZMM/Import10X-HelperFunctions_SeuratV3.R")
sink(file = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/Badder-Sebastian_HFpEF_model_mouse.RMD.log", append = TRUE, split = TRUE)
```

# 1.) Star default Filter
## 1.2) Define static parameters
```{r}
#Static Parameters 
Paths <- c("/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/104081-001-001/Solo.out/Gene/filtered/",
"/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/104081-001-002/Solo.out/Gene/filtered/",
"/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/104081-001-003/Solo.out/Gene/filtered/",
"/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/104081-001-004/Solo.out/Gene/filtered/",
"/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/104081-001-005/Solo.out/Gene/filtered/",
"/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/104081-001-006/Solo.out/Gene/filtered/"
)


Samplenames <- c("HFpEF-1","HFpEF-2","CTRL-1",
                 "CTRL-2","CTRL-3","HFpEF-3")
```


## 1.3) import and combine the raw cellranger counts with CCA
```{r}
SeuratObjectList <- list()
for (i in 1:length(Paths)) {
  SeuratObjectList[[i]]<-Importer(pathway = Paths[i],id = Samplenames[i], performNormalisation = TRUE, performVariableGeneDetection = TRUE, FilterCells = TRUE)
}
```

```{r}
tmpList<-list()
for (i in 1:length(SeuratObjectList)) {
  tmpid<-levels(Idents(SeuratObjectList[[i]][[1]]))
  #print(tmpid)
  print(paste(Samplenames[i],length(Idents(SeuratObjectList[[1]][[1]])), "Cell"))
  
  tmp<-SeuratObjectList[[i]][[1]]
  tmpList[[i]]<-tmp
  gg <- VlnPlot(object = tmp, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3, group.by = "orig.ident") + ggtitle(tmpid)
  print(gg)
  tmp<-ScaleData(object = tmp)
  tmp<-RunPCA(object = tmp, verbose = FALSE, ndims.print = 0)
  DimHeatmap(object = tmp, dims = 1:10, )
  gg<-ElbowPlot(tmp, ndims = 10) + labs(title=as.character(i))
  print(gg)
}
SeuratObjectList<-tmpList
```

## 1.4.) Integrate Data
```{r}
HFpEF_Mouse_Nuclei.anchors <- FindIntegrationAnchors(object.list = SeuratObjectList, dims = 1:10, k.filter = 20)
HFpEF_Mouse_Nuclei.combined <- IntegrateData(anchorset = HFpEF_Mouse_Nuclei.anchors, dims = 1:10)
```
## 1.5.) Cluster data
```{r}
DefaultAssay(object = HFpEF_Mouse_Nuclei.combined) <- "integrated"

# Run the standard workflow for visualization and clustering
HFpEF_Mouse_Nuclei.combined <- ScaleData(object = HFpEF_Mouse_Nuclei.combined, verbose = FALSE)
HFpEF_Mouse_Nuclei.combined <- RunPCA(object = HFpEF_Mouse_Nuclei.combined, npcs = 30, verbose = FALSE)
# t-SNE and Clustering
#FirstInMan.combined <- RunUMAP(object = FirstInMan.combined, reduction = "pca", dims = 1:20)
HFpEF_Mouse_Nuclei.combined <- RunTSNE(object = HFpEF_Mouse_Nuclei.combined, reduction = "pca", dims = 1:20)
HFpEF_Mouse_Nuclei.combined <- FindNeighbors(object = HFpEF_Mouse_Nuclei.combined, reduction = "pca", dims = 1:20)
HFpEF_Mouse_Nuclei.combined <- FindClusters(HFpEF_Mouse_Nuclei.combined, resolution = 0.5)
```


```{r }
condition<-c()
for (ident in HFpEF_Mouse_Nuclei.combined@meta.data$orig.ident) {
  tmp<-unlist(strsplit(ident,split = "-"))
  #currentBarcode<-paste0(tmp[2:length(tmp)],collapse = "_")
  condition<-c(condition,tmp[1])
}
names(condition)<-names(HFpEF_Mouse_Nuclei.combined@active.ident)
HFpEF_Mouse_Nuclei.combined$condition<-condition
```

```{r,fig.height=8, fig.width=15 }
DimPlot(object = HFpEF_Mouse_Nuclei.combined, label=T, pt.size = 0.1, do.return=TRUE)
DimPlot(object = HFpEF_Mouse_Nuclei.combined, group.by = "orig.ident", pt.size = 0.001, split.by = "condition")
DimPlot(object = HFpEF_Mouse_Nuclei.combined, group.by = "seurat_clusters", pt.size = 0.001, split.by = "condition")
DimPlot(object = HFpEF_Mouse_Nuclei.combined, group.by = "condition", pt.size = 0.001)
FeaturePlot(HFpEF_Mouse_Nuclei.combined, features = c("IL7R","CD14","MS4A1","CD8A","NKG7","FCGR3A","FCER1A","PPBP","CD4"), min.cutoff = 0, label = TRUE, label.size = 4)
FeaturePlot(HFpEF_Mouse_Nuclei.combined, features = c("IL7R","CD4"), min.cutoff = 0, label = TRUE, label.size = 4)

```
```{r}

```

```{r}
table(HFpEF_Mouse_Nuclei.combined$sample)
table(HFpEF_Mouse_Nuclei.combined$orig.ident)
table(HFpEF_Mouse_Nuclei.combined$condition)
table(HFpEF_Mouse_Nuclei.combined$seurat_clusters)
```






## 1.6.) Find Cluster specific Genes
```{r}
Idents(HFpEF_Mouse_Nuclei.combined)<-"seurat_clusters" 
HFpEF_Mouse_Nuclei.combined.markers<-FindAllMarkers(object = HFpEF_Mouse_Nuclei.combined, assay = "RNA", only.pos = TRUE)
TopGenesPerCluster<- HFpEF_Mouse_Nuclei.combined.markers %>% group_by(cluster) %>% top_n(5, avg_logFC)
```

```{r}
TopGenesPerCluster
```


```{r, fig.height=7, fig.width=15}
features<-unique(TopGenesPerCluster$gene)
DotPlot(HFpEF_Mouse_Nuclei.combined, features = rev(features), group.by = "seurat_clusters", assay = "RNA", ) + theme(axis.text.x = element_text(angle = 45))

#marker_genes = {'CD4 T cells':{'IL7R'},'CD14+ Monocytes':{'CD14',
#                 'LYZ'}, 'B cells':{'MS4A1'}, 'CD8 T cells':{'CD8A'},
#                 'NK cells':{'GNLY', 'NKG7'}, 'FCGR3A+ Monocytes':
#                 {'FCGR3A', 'MS4A7'}, 'Dendritic Cells':{'FCER1A',
#                 'CST3'}, 'Megakaryocytes':{'PPBP'}}

```

```{r}
#marker_genes<-c("GNLY","NKG7","IL7R","CD8A","MS4A1","FCGR3A","MS4A7","LYZ","CD14","CST3","FCER1A","PPBP")
marker_genes <- c("Pdgfra", "Col4a1", "Adamts5", "Lamb1", "Dpep1", "Ms4a4d", "Medag", "Col3a1", "Mmp2", "Dpt", "Dcn", "Dkk3", "Comp", "Tbx20",
            "Meox1", "Prg4", "Frzb", "Tnc", "Col1a1", "Lox", "Postn", "Acta2","Lyz2", "Lgals3", "Mrc1", "Cd68", "Cd14", "CD16", "Msr1", "Cd209a",
            "Cd83", "Napsa", "Cd74", "Ly6g", "Cxcr2", "Prox1", "Tie1", "Lyve1", "Cldn5", "Vwf", "Eng", "Emcn", "Fabp4", "Pecam1", "Cdh5",
            "Ccl5", "Nkg7", "Ptprc", "Klrc1", "Ctla4", "Klre1", "Cd3g", "Trdc", "Icos", "Cd3e", "Lat", "Lef1", "Tcf7", "Iglc1", "Pax5",
            "Iglc2", "Iglc3", "Cd79a", "Cd79b", "Cd19", "Plp1", "Kcna1", "Kcna2", "Cd59a", "Rgs5", "Tagln", "Myh11", "Vtn", "Notch3",
            "Pdgfrb", "Cspg4", "Des", "Pln", "Nkain4", "Krt8", "Krt19", "Krt18")
marker_genes <- c("Tnnt2", "Des", "Tntc", "Cdh4", "Mb","Cox6a2","Myl3",
"Tpm1","Tnni3","Myl2","Fabp3","Slc25a4","Actc1"
)

DotPlot(HFpEF_Mouse_Nuclei.combined, features = rev(marker_genes), group.by = "seurat_clusters", assay = "RNA", ) + theme(axis.text.x = element_text(angle = 90))
```

## 1.7.)Rename Idents
```{r}
Heart.combined <- RenameIdents(Heart.combined, `0` = "Cardiomiocytes", `1` = "Fibroblasts", `2` = "ECs", 
                               `3` = "Dentritic Cells", `4` = "Fibroblasts", `5` = "ECs", `6` = "Pericytes", `7` = "Dentritic Cells", `8` = "Fibroblasts", `9` = "ECs", 
                               `10` = "Cardiomiocytes", `11` = "Dentritic Cells", `12` = "ECs", `13` = "Fibroblasts/ECs",`14` = "Cardiomiocytes", 
                               `15` = "Cardiomiocytes", `16` = "SWL", `17` = "Cardiomiocytes", 
                               `18` = "Pericytes/ECs", `19` = "Dentritic Cells", `20` = "Cardiomiocytes/Fibroblasts")


#                     0             1           2           3           4                 5           6               7             8         9     
#clusterNames<-c("NK cells","CD4 T cells","CD8 T cells","CD4 T cells","B cells","FCGR3A+ Monocytes","NK cells","CD4 T cells","CD14+ Monocytes","NK cells",
#         10           11               12            13            14
#                "NK cells", "Plasma Cells","Dendritic Cells","CD4 T cells","CD4 T cells")
#Idents(FirstInMan.combined)<-"seurat_clusters"
#names(clusterNames) <- levels(FirstInMan.combined)
#FirstInMan.combined <- RenameIdents(FirstInMan.combined, clusterNames)


FirstInMan.combined <- RenameIdents(FirstInMan.combined,'0'="NK cells",'1'="CD4 T cells",'2'="CD8 T cells",'3'="CD4 T cells",
                                    '4'="B cells",'5'="FCGR3A+ Monocytes",'6'="NK cells",'7'="CD4 T cells",
                                    '8'="CD14+ Monocytes",'9'="NK cells",'10'="NK cells",'11'= "Plasma Cells",
                                    '12'="Dendritic Cells",'13'="CD4 T cells",'14'="CD4 T cells")
FirstInMan.combined$celltypes<-Idents(FirstInMan.combined)

```

```{r}
DimPlot(object = FirstInMan.combined, group.by = "celltypes", pt.size = 0.1, label = TRUE, label.size = 6)
DimPlot(object = FirstInMan.combined, group.by = "celltypes",split.by = "condition", pt.size = 0.1, label = TRUE, label.size = 6)

```


##1.8.) Generate barplot of cell per cluster per condition
```{r fig.height=5, fig.width=8, warning=FALSE}
# Counting celltypes in timepoints
library(stringr)
library(tidyr)

library(dplyr)
library(ggplot2)
library(scales)
library(Seurat)
V<- FirstInMan.combined@meta.data
condition.ordered<-str_sort(unique(FirstInMan.combined@meta.data$condition),numeric = TRUE)


V$condition<-factor(V$condition,levels = condition.ordered)
V$celltypes<-factor(V$celltypes)

Summary.Celltypes <- V %>% count(condition,celltypes,.drop = FALSE) %>% group_by(condition) %>%
  mutate(freq = n /sum(n)) %>% complete(celltypes,fill = list(n=0,freq=0))

Summary.Celltypes$celltypes <- factor(Summary.Celltypes$celltypes)
condition<-c()

#svg(filename = "/media/ATLAS_NGS_storage/Wesley/AnalysisDavid-2019/Unimputed/CD31+/Barplot-CellsperClusterPerSample.svg",width = 15, height = 10)
ggplot(Summary.Celltypes, aes(x=condition, y= freq, fill= condition))+
  geom_col(width = 0.9, color = "black")+
  facet_wrap(~celltypes, nrow = 2, scales = "free")+
  scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+
  theme(panel.background = element_blank(), axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust= 1, size = 8))
#dev.off()
```



##1.9.) Generate barplot of cell per cluster per condition
```{r fig.height=5, fig.width=8, warning=FALSE}
# Counting celltypes in timepoints
V<- FirstInMan.combined@meta.data
tmp2<-FirstInMan.combined@meta.data$orig.ident
tmp<-trimws(FirstInMan.combined@meta.data$orig.ident, which = "left", )
orig.ident.ordered<-factor(str_sort(unique(trimws(FirstInMan.combined@meta.data$orig.ident)),numeric = TRUE))

V$orig.ident<-factor(V$orig.ident,levels = orig.ident.ordered)
V$celltypes<-factor(V$celltypes)

Summary.Celltypes <- V %>% count(orig.ident, condition,celltypes,.drop = FALSE) %>% group_by(condition) %>%
  mutate(freq = n /sum(n)) %>% complete(celltypes,fill = list(n=0,freq=0))


tmp<-V %>% count(orig.ident, condition,celltypes,.drop = FALSE) 
Summary.Celltypes$celltypes <- factor(Summary.Celltypes$celltypes)

Summary.Celltypes$orig.ident<-factor(Summary.Celltypes$orig.ident,levels = orig.ident.ordered)
#condition<-c()
tmp<-Summary.Celltypes%>%arrange(condition)
#svg(filename = "/media/ATLAS_NGS_storage/Wesley/AnalysisDavid-2019/Unimputed/CD31+/Barplot-CellsperClusterPerSample.svg",width = 15, height = 10)
ggplot(Summary.Celltypes, aes(x=condition, y= freq, fill= orig.ident))+
  geom_col(width = 0.9, color = "black")+
  facet_wrap(~celltypes, nrow = 2, scales = "free")+
  scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+
  theme(panel.background = element_blank(), axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust= 1, size = 8))

```


##1.10.) Find DEG after Treatment
```{r}
table(FirstInMan.combined$condition)
Idents(FirstInMan.combined) <- "condition"
DEG_D1Placebo_vs_D4_Placebo <- FindMarkers(object = FirstInMan.combined, ident.1 = "D1_predose_Placebo", ident.2 = "D4_Placebo", assay = "RNA", slot = "data", logfc.threshold="0.1", test.use = "bimod",)
DEG_D1Predose_1.5_vs_D4_1.5 <- FindMarkers(object = FirstInMan.combined, ident.1 = "D1_predose_1.5", ident.2 = "D4_1.5", assay = "RNA", slot = "data", logfc.threshold="0.1", test.use = "bimod")

DEG_D1Placebo_vs_D4_Placebo$Gene<-rownames(DEG_D1Placebo_vs_D4_Placebo)
DEG_D1Predose_1.5_vs_D4_1.5$Gene<-rownames(DEG_D1Predose_1.5_vs_D4_1.5)

set1<-DEG_D1Placebo_vs_D4_Placebo[DEG_D1Placebo_vs_D4_Placebo$p_val<0.05,]
set2<-DEG_D1Predose_1.5_vs_D4_1.5[DEG_D1Predose_1.5_vs_D4_1.5$p_val<0.05,]
write.csv2(set1, file = "/media/Helios_scStorage/Wesley/103773-001/cellranger/Seurat3_Analysis_David/DEG_D1Placebo_vs_D4_Placebo.csv")
write.csv2(set2, file = "/media/Helios_scStorage/Wesley/103773-001/cellranger/Seurat3_Analysis_David/DEG_D1Predose_1.5_vs_D4_1.5.csv")


```

```{r}

celltypes<-levels(FirstInMan.combined$celltypes)
celltype<-celltypes[1]

table(FirstInMan.combined@)
for (celltype in celltypes) {
  df<-data.frame(Gene=mir92Targets)
  
  tmpSeurat<-subset(FirstInMan.combined, idents = celltype)
  Idents(tmpSeurat) <- "orig.ident"
  
  avg<-AverageExpression(tmpSeurat, assays = "RNA", features = mir92Targets, verbose = FALSE)
  avg$RNA<-exp(avg$RNA)
  if (length(avg$RNA)==length(unique(FirstInMan.combined$orig.ident))) {
    df$Tre_127_FC<-avg$RNA$Pat127_D4_1.5/avg$RNA$Pat127_D1_predose_1.5
    df$Tre_129_FC<-avg$RNA$Pat129_D4_1.5/avg$RNA$Pat129_D1_predose_1.5
    df$Tre_132_FC<-avg$RNA$Pat132_D4_1.5/avg$RNA$Pat132_D1_predose_1.5
    df$Tre_137_FC<-avg$RNA$Pat137_D4_1.5/avg$RNA$Pat137_D1_predose_1.5
    df$Tre_142_FC<-avg$RNA$Pat142_D4_1.5/avg$RNA$Pat142_D1_predose_1.5
    df$Pla_128_FC<-avg$RNA$Pat128_D4_Placebo/avg$RNA$Pat128_D1_predose_Placebo
    df$Pla_130_FC<-avg$RNA$Pat130_D4_Placebo/avg$RNA$Pat130_D1_predose_Placebo
    
    df_melted<-melt(df)
    gg <- ggplot(df_melted, aes(x=variable, y=value)) + 
      geom_boxplot() + scale_y_continuous(limits = c(0,2)) + 
      labs(title = celltype)
    print(gg)
  }
  else  {
    cat("Skipping ",celltype, "because not enough cells")
  }
  
}
tail(FirstInMan.combined@assays$RNA)
#loop over celltypes

#loop over patient
VlnPlot(FirstInMan.combined,features = c("GLRA1"))

```



##1.11.) Save and reload
```{r}
save.image("/media/Helios_scStorage/Wesley/103773-001/Workspace_12.11.19.R.RData")
load("/media/Helios_scStorage/Wesley/103773-001/Workspace_12.11.19.R.RData")

rm(HFpEF_Mouse_Nuclei.anchors, HFpEF_Mouse_Nuclei.combined, HFpEF_Mouse_Nuclei.combined.markers)
```



###################################################################################################
##----------------------------------------------------------------------------------------------##
###################################################################################################

# 2.) Star default Filter
## 2.2) Define static parameters
```{r}
#Static Parameters 
Paths <- c("/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/104081-001-001/Solo.out/Gene/filtered_matrix_emptyDrops/",
"/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/104081-001-002/Solo.out/Gene/filtered_matrix_emptyDrops/",
"/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/104081-001-003/Solo.out/Gene/filtered_matrix_emptyDrops/",
"/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/104081-001-004/Solo.out/Gene/filtered_matrix_emptyDrops/",
"/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/104081-001-005/Solo.out/Gene/filtered_matrix_emptyDrops/",
"/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/104081-001-006/Solo.out/Gene/filtered_matrix_emptyDrops/"
)


Samplenames <- c("HFpEF-1","HFpEF-2","CTRL-1",
                 "CTRL-2","CTRL-3","HFpEF-6")
```


## 2.3) import and combine the raw cellranger counts with CCA
```{r}
SeuratObjectList <- list()
for (i in 1:length(Paths)) {
  SeuratObjectList[[i]]<-Importer(pathway = Paths[i],id = Samplenames[i], performNormalisation = TRUE, performVariableGeneDetection = TRUE, FilterCells = TRUE)
}
```

```{r}
tmpList<-list()
for (i in 1:length(SeuratObjectList)) {
  tmpid<-levels(Idents(SeuratObjectList[[i]][[1]]))
  #print(tmpid)
  print(paste(Samplenames[i],length(Idents(SeuratObjectList[[1]][[1]])), "Cell"))
  
  tmp<-SeuratObjectList[[i]][[1]]
  tmpList[[i]]<-tmp
  gg <- VlnPlot(object = tmp, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3, group.by = "orig.ident") + ggtitle(tmpid)
  print(gg)
  tmp<-ScaleData(object = tmp)
  tmp<-RunPCA(object = tmp, verbose = FALSE, ndims.print = 0)
  DimHeatmap(object = tmp, dims = 1:10, )
  gg<-ElbowPlot(tmp, ndims = 10) + labs(title=as.character(i))
  print(gg)
}
SeuratObjectList<-tmpList
```

## 2.4.) Integrate Data
```{r}
HFpEF_Mouse_Nuclei.emptyDrop.anchors <- FindIntegrationAnchors(object.list = SeuratObjectList, dims = 1:10, k.filter = 20)
HFpEF_Mouse_Nuclei.emptyDrop.combined <- IntegrateData(anchorset = HFpEF_Mouse_Nuclei.emptyDrop.anchors, dims = 1:10)
```
## 2.5.) Cluster data
```{r}
DefaultAssay(object = HFpEF_Mouse_Nuclei.emptyDrop.combined) <- "integrated"

# Run the standard workflow for visualization and clustering
HFpEF_Mouse_Nuclei.emptyDrop.combined <- ScaleData(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, verbose = FALSE)
HFpEF_Mouse_Nuclei.emptyDrop.combined <- RunPCA(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, npcs = 30, verbose = FALSE)
# t-SNE and Clustering
HFpEF_Mouse_Nuclei.emptyDrop.combined <- RunUMAP(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, reduction = "pca", dims = 1:20)
HFpEF_Mouse_Nuclei.emptyDrop.combined <- RunTSNE(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, reduction = "pca", dims = 1:20)
HFpEF_Mouse_Nuclei.emptyDrop.combined <- FindNeighbors(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, reduction = "pca", dims = 1:20)
HFpEF_Mouse_Nuclei.emptyDrop.combined <- FindClusters(HFpEF_Mouse_Nuclei.emptyDrop.combined, resolution = 0.5, )
```


```{r }
condition<-c()
for (ident in HFpEF_Mouse_Nuclei.emptyDrop.combined@meta.data$orig.ident) {
  tmp<-unlist(strsplit(ident,split = "-"))
  #currentBarcode<-paste0(tmp[2:length(tmp)],collapse = "_")
  condition<-c(condition,tmp[1])
}
names(condition)<-names(HFpEF_Mouse_Nuclei.emptyDrop.combined@active.ident)
HFpEF_Mouse_Nuclei.emptyDrop.combined$condition<-condition
```

```{r,fig.height=8, fig.width=15 }
DimPlot(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, label=T, pt.size = 0.1, do.return=TRUE, label.size = 8)
DimPlot(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, group.by = "orig.ident", pt.size = 0.1, split.by = "condition")
DimPlot(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, group.by = "seurat_clusters", pt.size = 0.1, split.by = "condition", label = T, label.size = 8)
DimPlot(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, group.by = "condition", pt.size = 0.1)
FeaturePlot(HFpEF_Mouse_Nuclei.emptyDrop.combined, features = c("Il7r","Cd14","Ms4a1","Cd8a","Nkg7","Fcgr3a","Fcer1a","Ppbp","Cd4"), min.cutoff = 0)
FeaturePlot(HFpEF_Mouse_Nuclei.emptyDrop.combined, features = c("Ttn","Cd4"), min.cutoff = 0)

```
```{r}

```

```{r}
table(HFpEF_Mouse_Nuclei.emptyDrop.combined$sample)
table(HFpEF_Mouse_Nuclei.emptyDrop.combined$orig.ident)
table(HFpEF_Mouse_Nuclei.emptyDrop.combined$condition)
table(HFpEF_Mouse_Nuclei.emptyDrop.combined$)
```






## 2.6.) Find Cluster specific Genes
```{r}
Idents(HFpEF_Mouse_Nuclei.emptyDrop.combined)<-"seurat_clusters" 
HFpEF_Mouse_Nuclei.emptyDrop.combined.markers<-FindAllMarkers(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, assay = "RNA", only.pos = TRUE)
TopGenesPerCluster<- HFpEF_Mouse_Nuclei.emptyDrop.combined.markers %>% group_by(cluster) %>% top_n(3, avg_logFC)
```

```{r}
TopGenesPerCluster
```


```{r, fig.height=15, fig.width=10}
features<-unique(TopGenesPerCluster$gene)
DotPlot(HFpEF_Mouse_Nuclei.emptyDrop.combined, features = rev(features), group.by = "seurat_clusters", assay = "RNA", ) + theme(axis.text.x = element_text(angle = 0)) + coord_flip()

#marker_genes = {'CD4 T cells':{'IL7R'},'CD14+ Monocytes':{'CD14',
#                 'LYZ'}, 'B cells':{'MS4A1'}, 'CD8 T cells':{'CD8A'},
#                 'NK cells':{'GNLY', 'NKG7'}, 'FCGR3A+ Monocytes':
#                 {'FCGR3A', 'MS4A7'}, 'Dendritic Cells':{'FCER1A',
#                 'CST3'}, 'Megakaryocytes':{'PPBP'}}

```

```{r, fig.height=10, fig.width=8}
#marker_genes = {'Cardiomyocytes-A':{'',''}

#'CD4 T cells':{'IL7R'},'CD14+ Monocytes':{'CD14',
#                 'LYZ'}, 'B cells':{'MS4A1'}, 'CD8 T cells':{'CD8A'},
#                 'NK cells':{'GNLY', 'NKG7'}, 'FCGR3A+ Monocytes':
#                 {'FCGR3A', 'MS4A7'}, 'Dendritic Cells':{'FCER1A',
#                 'CST3'}, 'Megakaryocytes':{'PPBP'}}

marker_genes <- c("Myl3", "Mb", "Tnnt2",     #Cardiomyocytes (A)
                  "Ttn","Ryr2","Dmd",      #Cardiomyocytes (B)
                  "Kcnj3","Pam","Myh6",      #Cardiomyocytes (C)
                  "Rbpj","F13a1","Pid1",     #Immune Cells (A)
                  "Ptprc", "Dock2","Cd74",   #Immune Cells (B)
                  "Pcdh9","Abca8a","Gpc6",   #Fibroblasts
                  "Gsn","Dcn","Apoe",        #Fibroblasts (Low-Qual)
                  "Car3","Fabp4","Fam13a",   #Granulocytes
                  "Wdr17","Sulf1","Sox6",    #Neuronal Like
                  "Ccl21a","Reln","Mmrn1",   #Endothelial
                  "Dlc1","Mast4","Rgs5"      #Pericytes
)

Pnpla3


```
```{r}
marker_genes<-c("Kdr", "Vwf", "Fabp4","Cdh5","Pecam1", "Pdgfra", "Vcan", "Slc9a9", "Mctp1", "H2-Eb1")

DotPlot(HFpEF_Mouse_Nuclei.emptyDrop.combined, features = rev(marker_genes), group.by = "seurat_clusters", assay = "RNA", ) + theme(axis.text.x = element_text(angle = 0)) + coord_flip()
```

## 2.7.)Rename Idents
```{r}
table(Idents(HFpEF_Mouse_Nuclei.emptyDrop.combined))
Idents(HFpEF_Mouse_Nuclei.emptyDrop.combined)<-"seurat_clusters"
HFpEF_Mouse_Nuclei.emptyDrop.combined <- RenameIdents(HFpEF_Mouse_Nuclei.emptyDrop.combined, `0` = "Cardiomiocytes (A)", `1` = "Endothelial (A)", `2` = "Fibroblasts (A)", 
                               `3` = "Cardiomiocytes (B)", `4` = "Endothelial (B)", `5` = "Cardiomiocytes (C)", `6` = "Cardiomiocytes (D)", `7` = "Pericytes (A)", `8` = "Immune Cells (A)", `9` = "Endothelial (C)", 
                               `10` = "Cardiomiocytes (E)", `11` = "Endothelial (D)", `12` = "Fibroblasts (B)", `13` = "Pericytes (B)",`14` = "Fibroblasts (Low-Qual)", 
                               `15` = "Fibroblasts (C)", `16` = "Cardiomiocytes (F)", `17` = "Cardiomiocytes (G)", 
                               `18` = "Cardiomiocytes (Ttn-rich)", `19` = "X1", `20` = "X2", `21` = "X3" )

HFpEF_Mouse_Nuclei.emptyDrop.combined$celltypes_detailed<-Idents(HFpEF_Mouse_Nuclei.emptyDrop.combined)
```

```{r, fig.width=15, fig.height=10}
DimPlot(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, group.by = "celltypes_detailed", pt.size = 0.1, label = TRUE, label.size = 6)
DimPlot(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, group.by = "celltypes_detailed",split.by = "condition", pt.size = 0.1, label = TRUE, label.size = 6)
```


```{r}
table(Idents(HFpEF_Mouse_Nuclei.emptyDrop.combined))
Idents(HFpEF_Mouse_Nuclei.emptyDrop.combined)<-"seurat_clusters"
HFpEF_Mouse_Nuclei.emptyDrop.combined <- RenameIdents(HFpEF_Mouse_Nuclei.emptyDrop.combined, `0` = "Cardiomiocytes", `1` = "Endothelial", `2` = "Fibroblasts", `3` = "Cardiomiocytes", `4` = "Endothelial", `5` = "Cardiomiocytes", `6` = "Cardiomiocytes", `7` = "Pericytes", `8` = "Immune Cells", `9` = "Endothelial", `10` = "Cardiomiocytes", `11` = "Endothelial", `12` = "Fibroblasts", `13` = "Pericytes",`14` = "Fibroblasts", `15` = "Fibroblasts", `16` = "X1", `17` = "X2",`18` = "X3", `19` = "X4", `20` = "X5", `21` = "X6" )

HFpEF_Mouse_Nuclei.emptyDrop.combined$celltypes<-Idents(HFpEF_Mouse_Nuclei.emptyDrop.combined)
```


```{r, fig.width=15, fig.height=10}
DimPlot(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, group.by = "celltypes", pt.size = 0.1, label = TRUE, label.size = 6)
DimPlot(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, group.by = "celltypes",split.by = "condition", pt.size = 0.1, label = TRUE, label.size = 6)

```


##2.8.) Generate barplot of cell per cluster per condition
```{r fig.height=5, fig.width=8, warning=FALSE}
# Counting celltypes in timepoints
library(stringr)
library(tidyr)

library(dplyr)
library(ggplot2)
library(scales)
library(Seurat)


V<- HFpEF_Mouse_Nuclei.emptyDrop.combined@meta.data
condition.ordered<-str_sort(unique(HFpEF_Mouse_Nuclei.emptyDrop.combined@meta.data$condition),numeric = TRUE)


V$condition<-factor(V$condition,levels = condition.ordered)
V$celltypes<-factor(V$celltypes)

Summary.Celltypes <- V %>% count(condition,celltypes,.drop = FALSE) %>% group_by(condition) %>%
  mutate(freq = n /sum(n)) %>% complete(celltypes,fill = list(n=0,freq=0))

Summary.Celltypes$celltypes <- factor(Summary.Celltypes$celltypes)
condition<-c()

#svg(filename = "/media/ATLAS_NGS_storage/Wesley/AnalysisDavid-2019/Unimputed/CD31+/Barplot-CellsperClusterPerSample.svg",width = 15, height = 10)
ggplot(Summary.Celltypes, aes(x=condition, y= freq, fill= condition))+
  geom_col(width = 0.9, color = "black")+
  facet_wrap(~celltypes, nrow = 2, scales = "free")+
  scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+
  theme(panel.background = element_blank(), axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust= 1, size = 8))
#dev.off()
```



##2.9.) Generate barplot of cell per cluster per condition
```{r fig.height=5, fig.width=15, warning=FALSE}
# Counting celltypes in timepoints
V<- HFpEF_Mouse_Nuclei.emptyDrop.combined@meta.data
tmp2<-HFpEF_Mouse_Nuclei.emptyDrop.combined@meta.data$orig.ident
orig.ident.ordered<-factor(str_sort(unique(trimws(HFpEF_Mouse_Nuclei.emptyDrop.combined@meta.data$orig.ident)),numeric = TRUE))

V$orig.ident<-factor(V$orig.ident,levels = orig.ident.ordered)
V$celltypes<-factor(V$celltypes)

Summary.Celltypes <- V %>% count(orig.ident, condition,celltypes,.drop = FALSE) %>% group_by(condition) %>%
  mutate(freq = n /sum(n)) %>% complete(celltypes,fill = list(n=0,freq=0))


tmp<-V %>% count(orig.ident, condition,celltypes,.drop = FALSE) 
Summary.Celltypes$celltypes <- factor(Summary.Celltypes$celltypes)

Summary.Celltypes$orig.ident<-factor(Summary.Celltypes$orig.ident,levels = orig.ident.ordered)
#condition<-c()
tmp<-Summary.Celltypes%>%arrange(condition)
#svg(filename = "/media/ATLAS_NGS_storage/Wesley/AnalysisDavid-2019/Unimputed/CD31+/Barplot-CellsperClusterPerSample.svg",width = 15, height = 10)
ggplot(Summary.Celltypes, aes(x=orig.ident, y= freq, fill= orig.ident))+
  geom_col(width = 0.9, color = "black")+
  facet_wrap(~celltypes, nrow = 2, scales = "free")+
  scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+
  theme(panel.background = element_blank(), axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust= 1, size = 8))
```


##2.10.) Find DEG after Treatment
```{r}
table(HFpEF_Mouse_Nuclei.emptyDrop.combined$condition)
Idents(HFpEF_Mouse_Nuclei.emptyDrop.combined) <- "condition"
DEG_CTRL_HFpEF <- FindMarkers(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, ident.1 = "CTRL", ident.2 = "HFpEF", assay = "RNA", slot = "data", logfc.threshold="0.1", test.use = "bimod")


DEG_CTRL_HFpEF$Gene<-rownames(DEG_CTRL_HFpEF)


write.csv2(DEG_CTRL_HFpEF, file = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/DEG_CTRL_vs_HFpEF_AllCells.csv", row.names = TRUE)


```

```{r}

celltypes<-levels(FirstInMan.combined$celltypes)
celltype<-celltypes[1]

table(FirstInMan.combined@)
for (celltype in celltypes) {
  df<-data.frame(Gene=mir92Targets)
  
  tmpSeurat<-subset(FirstInMan.combined, idents = celltype)
  Idents(tmpSeurat) <- "orig.ident"
  
  avg<-AverageExpression(tmpSeurat, assays = "RNA", features = mir92Targets, verbose = FALSE)
  avg$RNA<-exp(avg$RNA)
  if (length(avg$RNA)==length(unique(FirstInMan.combined$orig.ident))) {
    df$Tre_127_FC<-avg$RNA$Pat127_D4_1.5/avg$RNA$Pat127_D1_predose_1.5
    df$Tre_129_FC<-avg$RNA$Pat129_D4_1.5/avg$RNA$Pat129_D1_predose_1.5
    df$Tre_132_FC<-avg$RNA$Pat132_D4_1.5/avg$RNA$Pat132_D1_predose_1.5
    df$Tre_137_FC<-avg$RNA$Pat137_D4_1.5/avg$RNA$Pat137_D1_predose_1.5
    df$Tre_142_FC<-avg$RNA$Pat142_D4_1.5/avg$RNA$Pat142_D1_predose_1.5
    df$Pla_128_FC<-avg$RNA$Pat128_D4_Placebo/avg$RNA$Pat128_D1_predose_Placebo
    df$Pla_130_FC<-avg$RNA$Pat130_D4_Placebo/avg$RNA$Pat130_D1_predose_Placebo
    
    df_melted<-melt(df)
    gg <- ggplot(df_melted, aes(x=variable, y=value)) + 
      geom_boxplot() + scale_y_continuous(limits = c(0,2)) + 
      labs(title = celltype)
    print(gg)
  }
  else  {
    cat("Skipping ",celltype, "because not enough cells")
  }
  
}
tail(FirstInMan.combined@assays$RNA)
#loop over celltypes

#loop over patient
VlnPlot(FirstInMan.combined,features = c("GLRA1"))

```



##2.11.) Save and reload
```{r}
save.image("/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/Workspace_25.06.20.RData")

#Save Seurat Object
saveRDS(HFpEF_Mouse_Nuclei.emptyDrop.combined, file = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/AllCells/SeuratObject_AllCells.25.06.20.Rds")
load("/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/Workspace_25.06.20.RData")
```

```{r}
source("/home/david/scRNA-SEQ-ZMM/Import10X-HelperFunctions_SeuratV3.R")



PlotClusterPrecentageBarplot(x = HFpEF_Mouse_Nuclei.emptyDrop.combined@meta.data$orig.ident,faceWrapeBy = HFpEF_Mouse_Nuclei.emptyDrop.combined@meta.data$celltypes, file = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/BarplotCelltypePerSample.svg", width = 20,height = 12)

PlotClusterPrecentageBarplot(x = HFpEF_Mouse_Nuclei.emptyDrop.combined@meta.data$orig.ident,faceWrapeBy = HFpEF_Mouse_Nuclei.emptyDrop.combined@meta.data$celltypes_detailed, file = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/2ndRun(104081)/starsolo/BarplotCelltypeDetailedPerSample.svg", width = 20,height = 12)

PlotClusterPrecentageBarplot(x=HFpEF_Mouse_Nuclei.emptyDrop.combined$seurat_clusters, faceWrapeBy = HFpEF_Mouse_Nuclei.emptyDrop.combined$orig.ident)
```

##2.12.)Cluster Profiler
```{r}

library(biomaRt)
####   Annotate COUNT Matrix ####


if(org=="hg19"){
  dataset = "hsapiens_gene_ensembl"
} else if (org=="hg38"|org=="hg38smallRNA") 
{dataset = "hsapiens_gene_ensembl" 
} else if (org=="mm10") 
{dataset = "mmusculus_gene_ensembl" 
} else if (org=="rn6") 
{dataset = "rnorvegicus_gene_ensembl" 
} else if (org=="duck1") 
{dataset = "aplatyrhynchos_gene_ensembl"} 

# Annotation
Anno = getBM(attributes = c("ensembl_gene_id",
                            "external_gene_name", 
                            "mirbase_accession",
                            "mirbase_id",
                            "entrezgene", 
                            "description",
                            "gene_biotype"),
             values = rownames(DEG_CTRL_HFpEF_indiv),
             filters = "external_gene_name",
             mart = useMart("ENSEMBL_MART_ENSEMBL",
                            host = "http://Jan2019.archive.ensembl.org",
                            dataset="mmusculus_gene_ensembl"))

names(Anno) = c("ENSEMBLE_ID","SYMBOL","MIRBASE_ACC","MIRBASE_ID","ENTREZID","DESCRIPTION","TYPE")

library(dplyr)
Anno = filter(Anno, !ENSEMBLE_ID == "") %>%
  group_by(ENSEMBLE_ID) %>%
  summarize(SYMBOL = do.call(paste, c(as.list(SYMBOL), sep=",")),
            ENTREZID = do.call(paste, c(as.list(ENTREZID), sep=",")),
            DESCRIPTION= do.call(paste, c(as.list(DESCRIPTION), sep=",")),
            MIRBASE_ACC= do.call(paste, c(as.list(MIRBASE_ACC), sep=",")),
            MIRBASE_ID= do.call(paste, c(as.list(MIRBASE_ID), sep=",")),
            TYPE= do.call(paste, c(as.list(TYPE), sep=",")))
rownames(Anno)= Anno$ENSEMBLE_ID

# GO Annotation (collapsed)

go.anno = getBM(attributes = c("ensembl_gene_id",
                               "go_id",
                               "name_1006",
                               "go_linkage_type"),
                values = rownames(DEG_CTRL_HFpEF_indiv),
                filters = "external_gene_name",
                useMart("ENSEMBL_MART_ENSEMBL",
                       host = "http://Jan2019.archive.ensembl.org",
                        dataset="mmusculus_gene_ensembl"))


go.anno.list = filter(go.anno, !go_id == "") %>%
  group_by(ensembl_gene_id) %>%
  summarize(go_id = do.call(paste, c(as.list(go_id), sep=",")),
            go_names = do.call(paste, c(as.list(name_1006), sep=",")))

Anno = merge.data.frame(Anno,go.anno.list,by.x =0,by.y = "ensembl_gene_id",all.x = T)
rownames(Anno)=Anno$ENSEMBLE_ID

Anno = Anno[,-1] 
```



```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
BiocManager::install("clusterProfiler")  
library(clusterProfiler)
library(DESeq2)


table(HFpEF_Mouse_Nuclei.emptyDrop.combined$condition)
table(HFpEF_Mouse_Nuclei.emptyDrop.combined$orig.ident)

Idents(HFpEF_Mouse_Nuclei.emptyDrop.combined)<-"condition"
<<<<<<< HEAD
Idents(HFpEF_Mouse_Nuclei.emptyDrop.combined)<-"orig.ident"

DEG_CTRL_HFpEF_indiv <- FindMarkers(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, ident.1 = "CTRL", ident.2 = "HFpEF", assay = "RNA", slot = "data", logfc.threshold="0.1", test.use = "DESeq2")
=======
DEG_CTRL_HFpEF_indiv <- FindMarkers(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, ident.1 = "CTRL", ident.2 = "HFpEF", test.use = "DESeq2")
>>>>>>> 92a353cc7790ffac50b7112389077a23037eba6c

DEG_CTRL_HFpEF_indiv <- FindMarkers(object = HFpEF_Mouse_Nuclei.emptyDrop.combined, ident.1 = c("CTRL-1","CTRL-2","CTRL-3"), ident.2 = c("HFpEF-1","HFpEF-2","HFpEF-6"), assay = "RNA", slot = "data", logfc.threshold="0.1", test.use = "DESeq2")

VlnPlot(HFpEF_Mouse_Nuclei.emptyDrop.combined, features = c("6030445D17Rik"), assay = "RNA", group.by = "orig.ident")


#Enrich KEGG DB
kegg <- compareCluster(geneCluster=cluster.entrez.list,  
                       organism= "mouse",
                       universe=na.omit(Anno$ENTREZID),
                       pvalueCutoff=0.05,
                       qvalueCutoff=0.05,  
                       pAdjustMethod ="BH",
                       fun="enrichKEGG")

if(exists("kegg")){
  
  cp.result = c(cp.result,list(kegg))
  names(cp.result)[[length(cp.result)]]="KeggDB"
}




```

