---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r}
install.packages('Seurat')
```


## 1.1) Import packages
```{r message=FALSE}
#load libraries
library(dplyr)
library(ggpubr)
library(Seurat)
require(scales)
library(tidyr)
library(monocle)
library(clu)
library(sciplot)
library(tidyr)
library(ggplot2)
library(stringr)

install.packages("sciplot")
source("/home/david/scRNA-SEQ-ZMM/Import10X-HelperFunctions_SeuratV3.R")
outputFolder<-"/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/"
sink(file = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/Badder-LNA92-vs-CTRL.Seurat3.rmd.log", append = TRUE, split = TRUE)
```

```{r}
# Quick load
load("/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/W")
```

## 1.2) Define static parameters
```{r}
#Static Parameters 

Sample.Paths <- c("/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/starsolo/104285-001-001Solo.out/Gene/filtered/",
                  "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/starsolo/104285-001-002Solo.out/Gene/filtered/",
                  "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/starsolo/104285-001-003Solo.out/Gene/filtered/",
                  "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/starsolo/104285-001-004Solo.out/Gene/filtered/",
                  "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/starsolo/104285-001-005Solo.out/Gene/filtered/",
                  "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/starsolo/104285-001-006Solo.out/Gene/filtered/",
                  "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/starsolo/104285-001-007Solo.out/Gene/filtered/",
                  "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/starsolo/104285-001-008Solo.out/Gene/filtered/")

Samplenames <- c("CO-1","92a-1","92a-2","92a-3","CO-2","92a-4","CO-3","CO-4")
```



```{r}
tmpList<-list()
SeuratObjectList <- list()
for (i in 1:length(Sample.Paths)) {
  tmpList<-Importer(pathway = Sample.Paths[i],id = Samplenames[i], FilterCells = TRUE)
  print(tmpList[[2]])
  SeuratObjectList[[i]]<-tmpList[[1]]
}
```



```{r}
SeuratObject.anchors <- FindIntegrationAnchors(object.list = SeuratObjectList, dims = 1:20)
SeuratObject.combined <- IntegrateData(anchorset = SeuratObject.anchors, dims = 1:20)
```
#INTEGRATED
```{r}
DefaultAssay(object = SeuratObject.combined) <- "integrated"

# Run the standard workflow for visualization and clustering
SeuratObject.combined <- ScaleData(object = SeuratObject.combined, verbose = FALSE)
SeuratObject.combined <- RunPCA(object = SeuratObject.combined, npcs = 30, verbose = FALSE)
# t-SNE and Clustering
SeuratObject.combined <- RunUMAP(object = SeuratObject.combined, reduction = "pca", dims = 1:20)
SeuratObject.combined <- FindNeighbors(object = SeuratObject.combined, reduction = "pca", dims = 1:20)
SeuratObject.combined <- FindClusters(SeuratObject.combined, resolution = 0.5)
```


```{r}
SeuratObject.combined_ClusterTree<-BuildClusterTree(object = SeuratObject.combined, assay = "RNA", verbose = T)
PlotClusterTree(SeuratObject.combined_ClusterTree)
```


####All Samples combined
```{r fig.height=10, fig.width=20}
require(cowplot)
# Visualization
p1<-DimPlot(object = SeuratObject.combined, reduction = "umap", group.by = "orig.ident",pt.size = 1)
p2<-DimPlot(object = SeuratObject.combined, reduction = "umap", label = TRUE,pt.size = 1, label.size = 9)
#p3<-DimPlot(object = SeuratObject.combined, reduction = "umap", group.by = "sample",pt.size = 2)
ggarrange(p1,p2)

DimPlot(object = SeuratObject.combined, reduction = "umap", label = TRUE, split.by = "orig.ident")
Idents(SeuratObject.combined)<-"seurat_clusters"
DimPlot(object = SeuratObject.combined, reduction = "umap", label = TRUE, split.by = "condition", label.size = 8, pt.size = 1)

```


Find Cluster specific Markers
```{r}
SeuratObject.combined.markers <- FindAllMarkers(object = SeuratObject.combined, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
top20<-SeuratObject.combined.markers %>% group_by(cluster) %>% top_n(n = 10, wt = avg_logFC)
write.csv(top20, file = paste0(outputFolder,"top20ClusterMarkers.csv"))
write.csv(SeuratObject.combined.markers, file = paste0(outputFolder,"ClusterMarkers.csv"))
```
```{r}
#top2<-SeuratObject.combined.markers %>% group_by(cluster) %>% top_n(n = 10, wt = avg_logFC)

VlnPlot(SeuratObject.combined, features = c("Lna92a"))
FeaturePlot(SeuratObject.combined, features = c("Ly6c2"), label = TRUE)
```

```{r}
Idents(SeuratObject.combined)<-"seurat_clusters"

VlnPlot(object = SeuratObject.combined, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3, pt.size = 0,)

Idents(SeuratObject.combined)<-"orig.ident"
VlnPlot(object = SeuratObject.combined, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3, pt.size = 0,)

FeaturePlot(SeuratObject.combined, features = "Ptprc")
```




```{r}
Idents(SeuratObject.combined)<-"condition"
DEG_CTRL_vs_92a<-FindMarkers(SeuratObject.combined, ident.1 = "CO", ident.2 = "92a")
```

```{r}
Idents(SeuratObject.combined)<-"seurat_clusters"

top20<-SeuratObject.combined.markers %>% group_by(cluster) %>% top_n(n = 3, wt = avg_logFC)
DotPlot(SeuratObject.combined, features = unique(top20$gene)) + theme(axis.text.x = element_text(angle = 90))
```


#Rename Idents
```{r}
Idents(SeuratObject.combined)<-"seurat_clusters"
table(Idents(SeuratObject.combined))
SeuratObject.combined <- RenameIdents(SeuratObject.combined, 
                                      `0` = "CMs", 
                                      `1` = "CMs", 
                                      `2` = "CMs", 
                                      `3` = "ECs", 
                                      `4` = "PCs", 
                                      `5` = "EC/FB", 
                                      `6` = "FBs", 
                                      `7` = "CMs", 
                                      `8` = "Immune",
                                      `9` = "CMs")


SeuratObject.combined$celltypes<-Idents(SeuratObject.combined)

DimPlot(SeuratObject.combined, label = T)
```

#DEG Ctrl vs LNA91s globally
```{r}
DefaultAssay(SeuratObject.combined)<-"RNA"

Idents(SeuratObject.combined)<-"condition"
#Idents(SeuratObject.combined)<-"seurat_clusters"
table(Idents(SeuratObject.combined))
DEG_CTRL_vs_92a<-FindMarkers(SeuratObject.combined, ident.1 = "CO", ident.2 = "92a",assay = "RNA", slot = "data", )
#FeaturePlot(SeuratObject.combined, features = rownames(DEG_Ctrl_vs_HFrEF)[1], split.by = "condition")

pvalues<-do_cluster_t_test(SeuratObject.combined, DEG_CTRL_vs_92a, group="condition",cluster = "orig.ident")
pvalues<-data.frame(clustered.ttest=unlist(pvalues))

DEG_CTRL_vs_92a.merged<-merge(x = DEG_CTRL_vs_92a, pvalues, by = "row.names")
write.csv2(DEG_CTRL_vs_92a.merged, file = paste0(outputFolder,"DEG_CTRL_vs_92a.AllCells.csv"))
```
#Calculate DEG per Cluster
```{r}
celltypes<-names(table(SeuratObject.combined$celltypes))
Idents(SeuratObject.combined)<-"celltypes"

finalTable<-data.frame()
genes<-data.frame(rownames(seurat.celltype@assays$RNA))
for (celltype in celltypes) {
  seurat.celltype<-subset(SeuratObject.combined, idents=c(celltype))
  
  Idents(seurat.celltype)<-"condition"
  DEG_CTRL_vs_92a.celltype<-FindMarkers(seurat.celltype, ident.1 = "CO", ident.2 = "92a",assay = "RNA", slot = "data", logfc.threshold = 0.1, min.pct = 0.1, test.use = "DESeq2")

  pvalues<-do_cluster_t_test(seurat.celltype, DEG_CTRL_vs_92a.celltype, group="condition",cluster = "orig.ident")
  pvalues<-data.frame(clustered.ttest=unlist(pvalues))

  DEG_CTRL_vs_92a.celltype.merged<-merge(x = DEG_CTRL_vs_92a.celltype, pvalues, by = "row.names")
  DEG_CTRL_vs_92a.celltype.merged$celltype<-celltype
  finalTable<-rbind(finalTable,DEG_CTRL_vs_92a.celltype.merged)
  
}

write.csv2(finalTable, file = paste0(outputFolder,"DEG_CTRL_vs_92a.PerCelltype_logFC>0.1_minPct>0.1.test=DESeq2.csv"), row.names = F)
```

#Barplot of Number of DEGs per Celltype
```{r}
n<- finalTable[finalTable$p_val<0.05,] %>% group_by(celltype) %>% count(celltype)
p1<-ggplot(n, aes(x=reorder(celltype, -n),y=n,)) +
       geom_bar(stat = "identity", fill="#f68060", alpha=.6, width=.4)+ coord_flip() + xlab("") * theme_bw() + labs(x="", y="Number of DEGs by DESeq2 pValue < 0.05")


n<- finalTable[finalTable$p_val_adj<0.05,] %>% group_by(celltype) %>% count(celltype)
p2<-ggplot(n, aes(x=reorder(celltype, -n),y=n,)) +
       geom_bar(stat = "identity", fill="#f68060", alpha=.6, width=.4)+ coord_flip() + xlab("") * theme_bw() + labs(x="", y="Number of DEGs by DESeq2 adjusted pValue < 0.05")

n<- finalTable[finalTable$clustered.ttest<0.05,] %>% group_by(celltype) %>% count(celltype)
p3<-ggplot(n, aes(x=reorder(celltype, -n),y=n,)) +
       geom_bar(stat = "identity", fill="#f68060", alpha=.6, width=.4)+ coord_flip() + xlab("") * theme_bw() + labs(x="", y="Number of DEGs by Clustered TTest pValue < 0.05")

ggarrange(p1,p2,p3)


```

```{r}
VlnPlot(SeuratObject.combined, features = c("Rnase1", "Myh6"), group.by = "celltypes", split.by = "orig.ident") + theme(legend.position = "bottom")
```


#Request plots for Stefanie
```{r}
#In CM: Ctgf, Fhl2
#In ECs: Zeb2, Ccnd1
#In Pericytes: Rgs5, Cd36
setwd(outputFolder)
getwd()


#UMAPS



#VLNPlots
geneList<-c("Ctgf","Fhl2","Zeb2","Ccnd1","Rgs5","Cd36")
geneList<-c("Ttn","Mhrt", "Fabp4","Egfl7","Pdgfrb","Col3a1","Klf4","Ptprc")
geneList<-c("Abca8a","Meg3","Gp49a","Lilrb4")


for (gene in geneList) {
  #by Cluster
  tmp<-paste0(outputFolder,"png/",gene,"-Violin.cluster.orig.ident.png")
  jpeg(filename = tmp, width = 750, height = 450)
  g<-VlnPlot(SeuratObject.combined, features = c(gene), group.by = "seurat_clusters", split.by = "orig.ident", pt.size = 0) + theme(legend.position="left")
  print(g)
  dev.off()
  
    tmp<-paste0(outputFolder,"png/",gene,"-Violin.cluster.png")
  jpeg(filename = tmp, width = 750, height = 450)
  g<-VlnPlot(SeuratObject.combined, features = c(gene), group.by = "seurat_clusters", pt.size = 0) + theme(legend.position="left")
  print(g)
  dev.off()
  #by Celltype
    tmp<-paste0(outputFolder,"png/",gene,"-Violin.png")
  jpeg(filename = tmp, width = 750, height = 450)
  g<-VlnPlot(SeuratObject.combined, features = c(gene), group.by = "celltypes", pt.size = 0) + theme(legend.position="left")
  print(g)
  dev.off()
  
      tmp<-paste0(outputFolder,"png/",gene,"-Violin.orig.ident.png")
  jpeg(filename = tmp, width = 750, height = 450)
  g<-VlnPlot(SeuratObject.combined, features = c(gene), group.by = "celltypes", split.by = "orig.ident", pt.size = 0) + theme(legend.position="left")
  print(g)
  dev.off()
  
  tmp<-paste0(outputFolder,"png/",gene,"-UMAP.png")
  jpeg(filename = tmp, width = 750, height = 450)
  g<-FeaturePlot(SeuratObject.combined, features = c(gene), label = T, pt.size = 1.5) + theme(legend.position="left")
  print(g)
  dev.off()
}

VlnPlot(SeuratObject.combined, features = c("Ctgf"), group.by = "celltypes", split.by = "orig.ident", pt.size = 0) + theme(legend.position="left")
VlnPlot(SeuratObject.combined, features = c("Fhl2"), group.by = "celltypes", split.by = "orig.ident", pt.size = 0) + theme(legend.position="left")

VlnPlot(SeuratObject.combined, features = c("Zeb2"), group.by = "celltypes", split.by = "orig.ident", pt.size = 0) + theme(legend.position="left")
VlnPlot(SeuratObject.combined, features = c("Ccnd1"), group.by = "celltypes", split.by = "orig.ident", pt.size = 0) + theme(legend.position="left")

VlnPlot(SeuratObject.combined, features = c("Rgs5"), group.by = "celltypes", split.by = "orig.ident", pt.size = 0) + theme(legend.position="left")
VlnPlot(SeuratObject.combined, features = c("Cd36"), group.by = "celltypes", split.by = "orig.ident", pt.size = 0) + theme(legend.position="left")

```




```{r}

## prepare data for cluster t.test from the deg list and do a cluster t-test
do_cluster_t_test <- function(seurat_subset, degs, group="condition", cluster="seurat_clusters"){
  gene_names<- names(table(rownames(degs)))
  #print(head(gene_names))
  p_values <- vector("list",length(gene_names))
  names(p_values) <- gene_names
  #gene_names <- row.names(cluster_subset)
  #if (celltype=="Adipocytes"){
  #  seurat_subset <- seurat_subset[,!seurat_subset$orig.ident=="D7"]
  #}
  group <- seurat_subset[[group]][,1]
  cluster <- seurat_subset[[cluster]][,1]
  for (gene in gene_names){
    y <- c(t(as.matrix(seurat_subset@assays$RNA[gene,])))
    test_info <- my.t.test.cluster(y, cluster, group)
    p_values[[gene]] <- test_info[nrow(test_info)]
  }
  return(p_values)
}

## added line 54-56 so that each group is tested if 
## only one ovbservation is present and throw an error
my.t.test.cluster <- function (y, cluster, group, conf.int = 0.95) 
{
  group <- as.factor(group)
  cluster <- as.factor(cluster)
  s <- !(is.na(y) | is.na(cluster) | is.na(group))
  y <- y[s]
  cluster <- cluster[s]
  group <- group[s]
  n <- length(y)
  if (n < 2) 
    stop("n<2")
  gr <- levels(group)
  if (length(gr) != 2) 
    stop("must have exactly two treatment groups")
  n <- table(group)
  nc <- tapply(cluster, group, function(x) length(unique(x)))
  bar <- tapply(y, group, mean)
  u <- unclass(group)
  y1 <- y[u == 1]
  y2 <- y[u == 2]
  c1 <- factor(cluster[u == 1])
  c2 <- factor(cluster[u == 2])
  b1 <- tapply(y1, c1, mean)
  b2 <- tapply(y2, c2, mean)
  m1 <- table(c1)
  m2 <- table(c2)
  if (any(names(m1) != names(b1)))
    stop("logic error 1")
  if (any(names(m2) != names(b2)))
    stop("logic error 2")
  if (any(m2 < 2))
    stop(paste("The following clusters contain only one observation:",
               paste(names(m2[m2 < 2]), collapse = " ")))
  if (any(m1 < 2))
    stop(paste("The following clusters contain only one observation:",
               paste(names(m1[m1 < 2]), collapse = " ")))
  M1 <- mean(y1)
  M2 <- mean(y2)
  ssc1 <- sum(m1 * ((b1 - M1)^2))
  ssc2 <- sum(m2 * ((b2 - M2)^2))
  if (nc[1] != length(m1))
    stop("logic error 3")
  if (nc[2] != length(m2))
    stop("logic error 4")
  df.msc <- sum(nc) - 2
  msc <- (ssc1 + ssc2)/df.msc
  v1 <- tapply(y1, c1, var)
  v2 <- tapply(y2, c2, var)
  ssw1 <- sum((m1 - 1) * v1)
  ssw2 <- sum((m2 - 1) * v2)
  df.mse <- sum(n) - sum(nc)
  mse <- (ssw1 + ssw2)/df.mse
  na <- (sum(n) - (sum(m1^2)/n[1] + sum(m2^2)/n[2]))/(sum(nc) - 
                                                        1)
  rho <- (msc - mse)/(msc + (na - 1) * mse)
  r <- max(rho, 0)
  C1 <- sum(m1 * (1 + (m1 - 1) * r))/n[1]
  C2 <- sum(m2 * (1 + (m2 - 1) * r))/n[2]
  v <- mse * (C1/n[1] + C2/n[2])
  v.unadj <- mse * (1/n[1] + 1/n[2])
  de <- v/v.unadj
  dif <- diff(bar)
  se <- sqrt(v)
  zcrit <- qnorm((1 + conf.int)/2)
  cl <- c(dif - zcrit * se, dif + zcrit * se)
  z <- dif/se
  P <- 2 * pnorm(-abs(z))
  stats <- matrix(NA, nrow = 20, ncol = 2, dimnames = list(c("N", 
                                                             "Clusters", "Mean", "SS among clusters within groups", 
                                                             "SS within clusters within groups", "MS among clusters within groups", 
                                                             "d.f.", "MS within clusters within groups", "d.f.", "Na", 
                                                             "Intracluster correlation", "Variance Correction Factor", 
                                                             "Variance of effect", "Variance without cluster adjustment", 
                                                             "Design Effect", "Effect (Difference in Means)", "S.E. of Effect", 
                                                             paste(format(conf.int), "Confidence limits"), "Z Statistic", 
                                                             "2-sided P Value"), gr))
  stats[1, ] <- n
  stats[2, ] <- nc
  stats[3, ] <- bar
  stats[4, ] <- c(ssc1, ssc2)
  stats[5, ] <- c(ssw1, ssw2)
  stats[6, 1] <- msc
  stats[7, 1] <- df.msc
  stats[8, 1] <- mse
  stats[9, 1] <- df.mse
  stats[10, 1] <- na
  stats[11, 1] <- rho
  stats[12, ] <- c(C1, C2)
  stats[13, 1] <- v
  stats[14, 1] <- v.unadj
  stats[15, 1] <- de
  stats[16, 1] <- dif
  stats[17, 1] <- se
  stats[18, ] <- cl
  stats[19, 1] <- z
  stats[20, 1] <- P
  attr(stats, "class") <- "t.test.cluster"
  stats
}
```


```{r, fig.width=18}
VlnPlot(SeuratObject.combined, features = c("Cd7","S100a9","S100a8")) #Neutrophils
VlnPlot(SeuratObject.combined, features = c("Ly6c2","Plac8","Clec4e","F10")) #Monocytes
VlnPlot(SeuratObject.combined, features = c("Cd79a","Cd79b","Mzb1","Tppp3","Cd9","S100a6","Fcer2a")) #B-Cells
VlnPlot(SeuratObject.combined, features = c("Nkg7","Klre1","Klra7","S100a6","Klrk1","Gzmb")) #NK
VlnPlot(SeuratObject.combined, features = c("Tcf7","Rag1","Ccr9","Ltb4r1","Sell","Lef1","Tnfrsf18","Cd134","Cd8a","Cd8b1", "Cd3g")) #T-Cells
VlnPlot(SeuratObject.combined, features = c("Ccl8","F13a1","Il1b","Ccl4","Cd9","Isg15","Irf7","Fn1")) #Macrophages
VlnPlot(SeuratObject.combined, features = c("Cd209a","Ifitm1","Ccr7","Fscn1","Pla2g2d","Vcam1", "CD74", "Cd209a")) #DC


FeaturePlot(SeuratObject.combined, features = c("Cd209a","Ifitm1","Ccr7","Fscn1","Pla2g2d","Vcam1", "Cd74", "Cd209a"), label=T) #DC


tmp<-data.frame(Gene=rownames(SeuratObject.combined@assays$RNA))


```







## 3.1.6) Barplot of cell per cluster
```{r fig.height=10, fig.width=15}
# Counting celltypes in timepoints
V<- SeuratObject.combined@meta.data
orig.ident.ordered<-str_sort(unique(SeuratObject.combined@meta.data$orig.ident),numeric = TRUE)
V$orig.ident<-factor(V$orig.ident,levels = orig.ident.ordered)
#V$res.0.6<-factor(V$celltypes)

Summary.Celltypes <- V %>% count(orig.ident,res.0.6,.drop = FALSE) %>% group_by(orig.ident) %>%
  mutate(freq = n /sum(n)) %>% complete(res.0.6,fill = list(n=0,freq=0))

Summary.Celltypes$res.0.6 <- factor(Summary.Celltypes$res.0.6)
condition<-c()
for (x in Summary.Celltypes$orig.ident) {
  tmp<-unlist(strsplit(x,split = "-"))
  cx<-paste0(tmp[1:length(tmp)-1],collapse = "-")
  
  condition<-c(condition,cx)
  
}
Summary.Celltypes$condition<-condition

#svg(filename = paste0(outputFolder,"/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForPaper/Barplot-CellsperClusterPerSample.svg"),width = 15, height = 10)
ggplot(Summary.Celltypes, aes(x=orig.ident, y= freq, fill= condition))+
  geom_col(width = 0.9, color = "black")+
  facet_wrap(~res.0.6, nrow = 1, scales = "free")+
  scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+
  theme(panel.background = element_blank(),
        strip.text = element_text(size=12),
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust= 1, size = 10))
#dev.off()
```


## 3.1.6) Barplot of cell per cluster
```{r fig.height=10, fig.width=15}
addCondition<-function(sumCelltypes){
  condition<-c()
  for (x in sumCelltypes$orig.ident) {
    tmp<-unlist(strsplit(x,split = "-"))
    cx<-paste0(tmp[1:length(tmp)-1],collapse = "-")
    condition<-c(condition,cx)
  }
  sumCelltypes$condition<-factor(condition)
  return(sumCelltypes)
}

# Counting celltypes in timepoints
V<- SeuratObject.combined@meta.data

#by seurat_clusters split by orig.ident
Summary.Celltypes <- V %>% count(orig.ident,seurat_clusters,.drop = FALSE) %>% group_by(orig.ident) %>%
  mutate(freq = n /sum(n))
Summary.Celltypes<-addCondition(Summary.Celltypes)
png(filename = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForLabMeeting/Barplot_PercentCellsPerClusterByOrigIdent.png", width = 900, height = 400 )
ggplot(Summary.Celltypes, aes(x=orig.ident, y= freq, fill= condition))+
  geom_col(width = 0.9, color = "black")+ 
  facet_wrap(~seurat_clusters, nrow = 1, scales = "free")+ scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+ theme(panel.background = element_blank(), strip.text = element_text(size=12),
        axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust= 1, size = 10))
dev.off()

#by seurat_clusters split by condition
Summary.Celltypes <- V %>% count(condition,seurat_clusters,.drop = FALSE) %>% group_by(condition) %>%
  mutate(freq = n /sum(n))
png(filename = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForLabMeeting/Barplot_PercentCellsPerClusterByCondition.png", width = 900, height = 400 )
ggplot(Summary.Celltypes, aes(x=condition, y= freq, fill= condition))+
  geom_col(width = 0.9, color = "black")+ 
  facet_wrap(~seurat_clusters, nrow = 1, scales = "free")+ scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+ theme(panel.background = element_blank(), strip.text = element_text(size=12),
        axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust= 1, size = 10))
dev.off()

#----------------------------------------------
#by celltypes split by orig.ident
Summary.Celltypes <- V %>% count(orig.ident,celltypes,.drop = FALSE) %>% group_by(orig.ident) %>%
  mutate(freq = n /sum(n))
Summary.Celltypes<-addCondition(Summary.Celltypes)
png(filename = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForLabMeeting/Barplot_PercentCellsPerCelltypeByOrigIdent.png", width = 900, height = 400 )
ggplot(Summary.Celltypes, aes(x=orig.ident, y= freq, fill= condition))+
  geom_col(width = 0.9, color = "black")+ 
  facet_wrap(~celltypes, nrow = 1, scales = "free")+ scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+ theme(panel.background = element_blank(), strip.text = element_text(size=12),
        axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust= 1, size = 10))
dev.off()

Summary.Celltypes <- V %>% count(condition,celltypes,.drop = FALSE) %>% group_by(condition) %>%
  mutate(freq = n /sum(n))
png(filename = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForLabMeeting/Barplot_PercentCellsPerCelltypeByCondition.png", width = 900, height = 400 )
ggplot(Summary.Celltypes, aes(x=condition, y= freq, fill= condition))+
  geom_col(width = 0.9, color = "black")+ 
  facet_wrap(~celltypes, nrow = 1, scales = "free")+ scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+ theme(panel.background = element_blank(), strip.text = element_text(size=12),
        axis.title.x = element_blank(), axis.text.x = element_text(angle = 45, hjust= 1, size = 10))
dev.off()
```





```{r}
cellNumbers<-dcast(Summary.Celltypes,formula = orig.ident ~ res.0.6, value.var = "n")
write.csv2(cellNumbers,file = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForPaper/CellContributionPerCelltype.csv")
```


#count Feature per Celltype
```{r}
V<- SeuratObject.combined@meta.data
orig.ident.ordered<-str_sort(unique(SeuratObject.combined@meta.data$orig.ident),numeric = TRUE)
V$orig.ident<-factor(V$orig.ident,levels = orig.ident.ordered)

tmp <- V %>% group_by(orig.ident, celltypes) %>% summarise(Mean_n_feature = mean(nFeature_RNA))
nFeatureRNAPerCelltype<-dcast(tmp,formula = orig.ident ~ celltypes, value.var = "Mean_n_feature")
write.csv2(nFeatureRNAPerCelltype,file="/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForPaper/CellNFeatureRNAPerCelltype.csv")

tmp <- tmp %>% mutate(Percent_n_feature = Mean_n_feature /sum(Mean_n_feature))
dcast(tmp,formula = orig.ident ~ celltypes, value.var = "Percent_n_feature")

condition<-c()
for (x in tmp$orig.ident) {
  t<-unlist(strsplit(x,split = "-"))
  cx<-paste0(t[1:length(t)-1],collapse = "-")
  condition<-c(condition,cx)
}
tmp$condition<-condition

png(filename = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForLabMeeting/Barplot_PercentRNAsPerCelltypeByCondition.png", width = 900, height = 400 )
ggplot(tmp, aes(x=orig.ident, y= Percent_n_feature, fill= condition))+
  geom_col(width = 0.9, color = "black")+ facet_wrap(~celltypes, nrow = 1, scales = "free")+
  scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+
  theme(panel.background = element_blank(),strip.text = element_text(size=12), axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust= 1, size = 10))
dev.off()
```



```{r}
table(SeuratObject.combined$condition)
#names(SeuratObject.combined$condition)
```




```{r}
SeuratObject.combined<-ScaleData(SeuratObject.combined)
VlnPlot(SeuratObject.combined, features = "Ubc", group.by = "orig.ident", slot = "data", assay = "RNA")
SeuratObject.combined@assays$RNA@
```

#Create Plots for Paper
#UMAP Plot
```{r}
png(filename = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForPaper/UMAP_celltypes.png", width = 900,
    height = 600 )
DimPlot(SeuratObject.combined, label = T, label.size = 8, pt.size = 1) + theme(legend.position = "none")
dev.off()
```

#DotPlot
```{r}
png(filename = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForPaper/Dotplot_celltypes.png", width = 900,
    height = 600 )
DotPlot(SeuratObject.combined, features = unique(top20$gene), assay = "RNA", scale.min = 0, ) + theme(axis.text.x = element_text(angle = 90))
dev.off()

```

#Maker genes Feature plot
```{r}
genes<-c("Pdgfrb","Rgs5","Cspg4","Cd36","Ccnd1")


DefaultAssay(SeuratObject.combined)<-"RNA"
#Idents(SeuratObject.combined)<-"seurat_clusters"
plotList<-list()
for (i in seq_along(genes)) {
  g<-FeaturePlot(SeuratObject.combined, features = c(genes[[i]]), label.size = 4, label = T, min.cutoff = 0, slot = "data")  + theme(legend.position = "none")
  plotList[[i]]<-g

}
ggarrange(plotlist = plotList, nrow = 1)
```

#Maker genes Feature plot
```{r}
genes<-c("Pdgfrb","Rgs5","Cspg4","Cd36","Ccnd1")


DefaultAssay(SeuratObject.combined)<-"RNA"
#Idents(SeuratObject.combined)<-"seurat_clusters"
plotList<-list()
for (i in seq_along(genes)) {
  g<-VlnPlot(SeuratObject.combined, features = c(genes[[i]]), group.by = "celltypes", split.by = "condition", assay = "RNA", slot = "data", pt.size = 0.1) + theme(legend.position = "bottom")
  plotList[[i]]<-g

}
ggarrange(plotlist = plotList, nrow = 1)
```
#Maker genes Feature plot only in reclustered PC's
```{r}
genes<-c("Pdgfrb","Rgs5","Cspg4","Cd36","Ccnd1")


DefaultAssay(SeuratObject.combined)<-"RNA"
#Idents(SeuratObject.combined)<-"seurat_clusters"
plotList<-list()
for (i in seq_along(genes)) {
  g<-VlnPlot(Seurat.PCs, features = c(genes[[i]]), group.by = "seurat_clusters", split.by = "condition", assay = "RNA", slot = "data", pt.size = 0.1) + theme(legend.position = "bottom")
  plotList[[i]]<-g

}
ggarrange(plotlist = plotList, nrow = 1)
```

Calculate statistics for the requested genes
```{r}
Idents(SeuratObject.combined)<-"orig.ident"
AverageGeneExpression_AllCells<-AverageExpression(SeuratObject.combined, features = c("Pdgfrb","Rgs5","Cspg4","Cd36","Ccnd1"), assays = "RNA")[[1]] %>% select(sort(current_vars()))

for (crow in rownames(AverageGeneExpression)) {
  AverageGeneExpression_AllCells[crow, "mean92a"] <- mean(as.numeric(AverageGeneExpression_AllCells[crow,1:4]))
  AverageGeneExpression_AllCells[crow, "meanCo"] <- mean(as.numeric(AverageGeneExpression_AllCells[crow,5:8]))
  AverageGeneExpression_AllCells[crow, "sem92a"] <- se(as.numeric(AverageGeneExpression_AllCells[crow,1:4]))
  AverageGeneExpression_AllCells[crow, "semCo"] <- se(as.numeric(AverageGeneExpression_AllCells[crow,5:8]))
}
write.csv2(AverageGeneExpression_AllCells,file = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForPaper/MargerGenes_allCells.tsv")
```

```{r}
#
Idents(SeuratObject.combined)<-"celltypes"
Seurat.PCs<-subset(SeuratObject.combined, idents="PCs")
Idents(SeuratObject.combined)<-"orig.ident"

#Recluster PCs
# Run the standard workflow for visualization and clustering
Seurat.PCs <- FindVariableFeatures(object = Seurat.PCs, verbose = FALSE)
Seurat.PCs <- ScaleData(object = Seurat.PCs,verbose = FALSE)
Seurat.PCs <- RunPCA(object = Seurat.PCs, npcs = 30, verbose = FALSE)
# t-SNE and Clustering
Seurat.PCs <- RunUMAP(object = Seurat.PCs, reduction = "pca", dims = 1:20)
Seurat.PCs <- FindNeighbors(object = Seurat.PCs, reduction = "pca", dims = 1:20)
Seurat.PCs <- FindClusters(Seurat.PCs, resolution = 0.3)
DimPlot(Seurat.PCs, group.by = "seurat_clusters")


AverageGeneExpression_PCs<-AverageExpression(Seurat.PCs, features = c("Pdgfrb","Rgs5","Cspg4","Cd36","Ccnd1"), assays = "RNA")[[1]] %>% select(sort(current_vars()))

for (crow in rownames(AverageGeneExpression)) {
  AverageGeneExpression_PCs[crow, "mean92a"] <- mean(as.numeric(AverageGeneExpression_PCs[crow,1:4]))
  AverageGeneExpression_PCs[crow, "meanCo"] <- mean(as.numeric(AverageGeneExpression_PCs[crow,5:8]))
  AverageGeneExpression_PCs[crow, "sem92a"] <- se(as.numeric(AverageGeneExpression_PCs[crow,1:4]))
  AverageGeneExpression_PCs[crow, "semCo"] <- se(as.numeric(AverageGeneExpression_PCs[crow,5:8]))
}
write.csv2(AverageGeneExpression_PCs,file = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForPaper/MargerGenes_PCs.tsv")
```


```{r}
Gene<-c("Gene1","Gene2","Gene1","Gene2")
count1<-c(12,14,16,34)
count2<-c(4,7,9,23)
count3<-c(36,22,54,12)
count4<-c(12,24,35,23)
Species<-c("A","A","B","B")
df<-data.frame(Gene,count1,count2,count3,count4,Species)



data <- data.frame(
  name=letters[1:5],
  value=sample(seq(4,15),5),
  sd=c(1,0.2,3,2,4)
)

# Most basic error bar
ggplot(data) +
    geom_bar( aes(x=name, y=value), stat="identity", fill="skyblue", alpha=0.7) +
    geom_errorbar( aes(x=name, ymin=value-sd, ymax=value+sd), width=0.4, colour="orange", alpha=0.9, size=1.3)
```

```{r}
celltypes<-names(table(SeuratObject.combined$celltypes))
Idents(SeuratObject.combined)<-"celltypes"

finalTable<-data.frame()
genes<-c("Pdgfrb","Rgs5","Cspg4","Cd36","Ccnd1")
for (celltype in celltypes) {
  seurat.celltype<-subset(SeuratObject.combined, idents=c(celltype))
  
  Idents(seurat.celltype)<-"condition"
  DEG_CTRL_vs_92a.celltype<-FindMarkers(seurat.celltype, ident.1 = "CO", ident.2 = "92a",assay = "RNA", slot = "data",logfc.threshold = 0, features = genes)

  pvalues<-do_cluster_t_test(seurat.celltype, DEG_CTRL_vs_92a.celltype, group="condition",cluster = "orig.ident")
  pvalues<-data.frame(clustered.ttest=unlist(pvalues))

  DEG_CTRL_vs_92a.celltype.merged<-merge(x = DEG_CTRL_vs_92a.celltype, pvalues, by = "row.names")
  DEG_CTRL_vs_92a.celltype.merged$celltype<-celltype
  finalTable<-rbind(finalTable,DEG_CTRL_vs_92a.celltype.merged)
  
}

write.csv2(finalTable, file = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForPaper/DEG_CTRL_vs_92a.MarkerGenes-StefaniePerCelltype.csv", row.names = F)
```






#Subcluster Fibroblasts
```{r}
Idents(SeuratObject.combined)<-"celltypes"
table(Idents(SeuratObject.combined))
FB.Seurat<-subset(SeuratObject.combined,idents=c("FBs"))

DefaultAssay(object = FB.Seurat) <- "RNA"

# Run the standard workflow for visualization and clustering
FB.Seurat <- ScaleData(object = FB.Seurat, verbose = FALSE)
FB.Seurat <- RunPCA(object = FB.Seurat, npcs = 30, verbose = FALSE)
# t-SNE and Clustering
FB.Seurat <- RunUMAP(object = FB.Seurat, reduction = "pca", dims = 1:5)
FB.Seurat <- FindNeighbors(object = FB.Seurat, reduction = "pca", dims = 1:5)
FB.Seurat <- FindClusters(FB.Seurat)
```


```{r}
DimPlot(FB.Seurat, group.by = "orig.ident")
DimPlot(FB.Seurat, group.by = "condition")

```


```{r}
tmp<-data.frame(rownames(SeuratObject.combined))
```


```{r}
table(SeuratObject.combined$celltypes)
```



```{r}
save.image(file = paste0(outputFolder,"Workspace_21.12.20.RData"))
saveRDS(SeuratObject.combined, file = paste0(outputFolder,"SeuratObject_scNUCSEQ_CTRL_LNA92a_Badder_21.12.20.RData"))

cat(outputFolder)
```
```{r}
load("/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/Workspace_21.12.20.RData")
```

```{r}
load("/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/Seurat3.RData")
```


#Plots for Labemmeting
```{r}
png(filename = "/media/Helios_scStorage/Badder_Sebastian_HfPef_Model/104285/Seurat3/PlotsForLabMeeting/UMAP_orig.ident.png", width = 900, height = 600 )
#DimPlot(SeuratObject.combined, label = T, label.size = 12, pt.size = 1, group.by = "seurat_clusters") + theme
DimPlot(SeuratObject.combined, label = F, label.size = 8, pt.size = 1, group.by = "orig.ident") 
dev.off()
```
