---
title: "Patients with Chip mutations (Seurat3)"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---
  
# 1.) Import packages
```{r message=FALSE}
#load libraries
library(dplyr)
library(ggpubr)
library(reshape2)
require(scales)
library(ggplot2)

 
source("/home/david/scRNA-SEQ-ZMM/Import10X-HelperFunctions_SeuratV3.R")
sink(file = "/media/Helios_scStorage/Wesley/11275/starSolo/ChipMutations_filteredByStar.rmd.log", append = TRUE, split = TRUE)
```


## 1.2) Define static parameters
```{r}
#Static Parameters 
Paths <- c(
    "/media/Helios_scStorage/Wesley/11275/starSolo/HF1Solo.out/Gene/filtered/",
    "/media/Helios_scStorage/Wesley/11275/starSolo/HF2Solo.out/Gene/filtered/",
    "/media/Helios_scStorage/Wesley/11275/starSolo/HF3Solo.out/Gene/filtered/",
    "/media/Helios_scStorage/Wesley/11275/starSolo/HF4Solo.out/Gene/filtered/",
    "/media/Helios_scStorage/Wesley/11275/starSolo/HF5Solo.out/Gene/filtered/",
    "/media/Helios_scStorage/Wesley/11275/starSolo/HF6Solo.out/Gene/filtered/",
    "/media/Helios_scStorage/Wesley/11275/starSolo/HF7Solo.out/Gene/filtered/",
    "/media/Helios_scStorage/Wesley/11275/starSolo/HF8Solo.out/Gene/filtered/",
    "/media/Helios_scStorage/Wesley/11275/starSolo/HF9Solo.out/Gene/filtered/",
    "/media/Helios_scStorage/Wesley/11275/starSolo/HF10Solo.out/Gene/filtered/",
    "/media/Helios_scStorage/Wesley/11275/starSolo/HF11Solo.out/Gene/filtered/"
)


Samplenames <- c("CHIP1",
"Control1",
"Control2",
"Control3",
"CHIP2",
"Control4",
"CHIP3",
"Moderate",
"Control5",
"CHIP4",
"CHIP5")
```


```{r}
#Static Parameters 
Paths <- c(
    "/media/Helios_scStorage/Wesley/11275/starSolo/HF1Solo.out/Gene/filtered/"
)


Samplenames <- c("CHIP1")
```



## 1.3) import and combine the raw cellranger counts with CCA
```{r}
SeuratObjectList <- list()
for (i in 1:length(Paths)) {
  importerList<-Importer(pathway = Paths[i],id = Samplenames[i], performNormalisation = TRUE, performVariableGeneDetection = TRUE, FilterCells = TRUE)
  SeuratObjectList[[i]]<-importerList[1]
  gg<-importerList[[2]]
  print(gg)
}
```

#Filter cells with percent.mito < 0,2 & nFeature_RNA > 300 & top 5% with highest nFeature_RNA
```{r}
for (i in 1:lengt(SeuratObjectList)) {
  tmpSeuratObject<-SeuratObjectList[[i]]
  tmpSeuratObject<- subset(x = tmpSeuratObject, subset = nFeature_RNA > 300 & percent.mito < 0.2)
}
```




```{r}
ChipPatients_filteredStar.anchors <- FindIntegrationAnchors(object.list = SeuratObjectList, dims = 1:10, k.filter = 20)
ChipPatients_filteredStar.combined <- IntegrateData(anchorset = ChipPatients_filteredStar.anchors, dims = 1:10)


DefaultAssay(object = ChipPatients_filteredStar.combined) <- "integrated"

# Run the standard workflow for visualization and clustering
ChipPatients_filteredStar.combined <- ScaleData(object = ChipPatients_filteredStar.combined, verbose = FALSE)
ChipPatients_filteredStar.combined <- RunPCA(object = ChipPatients_filteredStar.combined, npcs = 30, verbose = FALSE)
# t-SNE and Clustering
#FirstInMan.combined <- RunUMAP(object = FirstInMan.combined, reduction = "pca", dims = 1:20)
ChipPatients_filteredStar.combined <- RunTSNE(object = ChipPatients_filteredStar.combined, reduction = "pca", dims = 1:20)
ChipPatients_filteredStar.combined <- FindNeighbors(object = ChipPatients_filteredStar.combined, reduction = "pca", dims = 1:20)
ChipPatients_filteredStar.combined <- FindClusters(ChipPatients_filteredStar.combined, resolution = 0.5)
save.image("/media/Helios_scStorage/Wesley/11275/starSolo/Workspace_13.01.20.RData")
```



```{r }
condition<-c()
for (ident in ChipPatients_filteredStar.combined@meta.data$orig.ident) {
  #tmp<-unlist(strsplit(ident,split = "_"))
  #currentBarcode<-paste0(tmp[2:length(tmp)],collapse = "_")
  currentBarcode <- substr(ident, 1, nchar(ident)-1)
  condition<-c(condition,currentBarcode)
}
names(condition)<-names(ChipPatients_filteredStar.combined@active.ident)
ChipPatients_filteredStar.combined$condition<-condition
```

#Quality Checks
```{r}
# Define an order of cluster identities
my_levels <- c("CHIP1","CHIP2","CHIP3","CHIP4","CHIP5","Control1","Control2","Control3","Control4","Control5","Moderate")

# Relevel object@ident
Idents(ChipPatients_filteredStar.combined) <- factor(x = Idents(ChipPatients_filteredStar.combined), levels = my_levels)
Idents(ChipPatients.combined) <- factor(x = Idents(ChipPatients.combined), levels = my_levels)

ChipPatients_filteredStar.combined$seurat_clusters

VlnPlot(ChipPatients.combined, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3,pt.size = 0)
VlnPlot(ChipPatients_filteredStar.combined, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3,pt.size = 0)

Idents(ChipPatients_filteredStar.combined) <- "seurat_clusters"
Idents(ChipPatients.combined) <-  "seurat_clusters"
VlnPlot(ChipPatients.combined, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3,pt.size = 0,)
VlnPlot(ChipPatients_filteredStar.combined, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3,pt.size = 0)

table(ChipPatients.combined$orig.ident)
Features <- combined@meta.data$nFeature_RNA
Count <- combined@meta.data$nCount_RNA
Percent.mito <- combined@meta.data$percent.mito

MT <- data.frame(sample = combined@meta.data$sample, 
                 Features = combined@meta.data$nFeature_RNA,
                 Count = combined@meta.data$nCount_RNA,
                 Percent.mito = combined@meta.data$percent.mito)

library(reshape2)
MT.melt <- melt(MT)

ggplot(MT.melt, aes(x=sample, y= value, fill= sample))+
  geom_jitter(height = 0, alpha = 0.8, color = "grey40", width = .3)+
  geom_violin(scale = "width")+
  facet_wrap(~variable, scales = "free_y")+
  theme_pubr()+
  theme(axis.title.x = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank())+
  scale_fill_manual(values = c("beige", "dark red", "blue", "dark green","yellow","orange","grey"))

```


```{r,fig.height=8, fig.width=15 }
DimPlot(object = ChipPatients_filteredStar.combined, label=T, pt.size = 0.1, do.return=TRUE)
DimPlot(object = ChipPatients_filteredStar.combined, group.by = "orig.ident", pt.size = 0.001, split.by = "condition")
DimPlot(object = ChipPatients_filteredStar.combined, group.by = "seurat_clusters", pt.size = 0.001, split.by = "condition")
DimPlot(object = ChipPatients_filteredStar.combined, group.by = "condition", pt.size = 0.001)
FeaturePlot(ChipPatients_filteredStar.combined, features = c("IL7R","CD14","MS4A1","CD8A","NKG7","FCGR3A","FCER1A","PPBP","CD4"), min.cutoff = 0, label = TRUE, label.size = 4)
FeaturePlot(ChipPatients_filteredStar.combined, features = c("IL7R","CD4"), min.cutoff = 0, label = TRUE, label.size = 4)

```


#Find Cluster specific Genes
```{r}
Idents(ChipPatients_filteredStar.combined)<-"seurat_clusters" 
ChipPatients_filteredStar.markers<-FindAllMarkers(object = ChipPatients_filteredStar.combined, assay = "RNA", only.pos = TRUE)
TopGenesPerCluster<- ChipPatients_filteredStar.markers %>% group_by(cluster) %>% top_n(4, avg_logFC)
```

```{r}
features<-unique(TopGenesPerCluster$gene)
DotPlot(ChipPatients_filteredStar.combined, features = rev(features), group.by = "seurat_clusters", assay = "RNA", ) + theme(axis.text.x = element_text(angle = 90))

#marker_genes = {'CD4 T cells':{'IL7R'},'CD14+ Monocytes':{'CD14',
#                 'LYZ'}, 'B cells':{'MS4A1'}, 'CD8 T cells':{'CD8A'},
#                 'NK cells':{'GNLY', 'NKG7'}, 'FCGR3A+ Monocytes':
#                 {'FCGR3A', 'MS4A7'}, 'Dendritic Cells':{'FCER1A',
#                 'CST3'}, 'Megakaryocytes':{'PPBP'}}


marker_genes<-c("GNLY","NKG7","IL7R","CD8A","MS4A1","FCGR3A","MS4A7","LYZ","CD14","CST3","FCER1A","PPBP","CD4", "CD79A")
marker_genes<-c( "CD79A","CD79B", "NCAM1")
DotPlot(ChipPatients_filteredStar.combined, features = rev(marker_genes), group.by = "seurat_clusters", assay = "RNA", ) + theme(axis.text.x = element_text(angle = 90))
```


#Rename Idents
```{r}

#new ones
ChipPatients_filteredStar.combined <- RenameIdents(ChipPatients_filteredStar.combined,'0'="CD14+ Monocytes",'1'="CD14+ Monocytes",'2'="NK cells",'3'="CD8 T cells",
                                                        '4'="T cells",'5'="T cells",'6'="CD14+ Monocytes",'7'="FCGR3A+ Monocytes",
                                                        '8'="CD8 T cells",'9'="B cells",'10'="Megakaryocytes",'11'= "CD14+ Monocytes(^Neat1)",
                                                        '12'="^MT-CO1",'13'="CD14+ Monocytes",'14'="Dendritic Cells", '15'="CD14+ Monocytes",
                                                        '16'="X1(^STMN1,^TUBA1B)",'17'="X2(^TCF4)",'18'="B cells")


ChipPatients_filteredStar.combined$celltypes<-Idents(ChipPatients_filteredStar.combined)

```

```{r}
DimPlot(object = ChipPatients_filteredStar.combined, group.by = "celltypes", pt.size = 0.1, label = TRUE, label.size = 6)
DimPlot(object = ChipPatients_filteredStar.combined, group.by = "celltypes",split.by = "condition", pt.size = 0.1, label = TRUE, label.size = 6)

```


#### Generate barplot of cell per cluster per condition
```{r fig.height=5, fig.width=8, warning=FALSE}
# Counting celltypes in timepoints
library(stringr)
library(tidyr)

library(dplyr)
library(ggplot2)
library(scales)
library(Seurat)
V<- ChipPatients_filteredStar.combined@meta.data
condition.ordered<-str_sort(unique(ChipPatients_filteredStar.combined@meta.data$condition),numeric = TRUE)


V$condition<-factor(V$condition,levels = condition.ordered)
V$celltypes<-factor(V$celltypes)

Summary.Celltypes <- V %>% count(condition,celltypes,.drop = FALSE) %>% group_by(condition) %>%
  mutate(freq = n /sum(n)) %>% complete(celltypes,fill = list(n=0,freq=0))

Summary.Celltypes$celltypes <- factor(Summary.Celltypes$celltypes)
condition<-c()

#svg(filename = "/media/ATLAS_NGS_storage/Wesley/AnalysisDavid-2019/Unimputed/CD31+/Barplot-CellsperClusterPerSample.svg",width = 15, height = 10)
ggplot(Summary.Celltypes, aes(x=condition, y= freq, fill= condition))+
  geom_col(width = 0.9, color = "black")+
  facet_wrap(~celltypes, nrow = 2, scales = "free")+
  scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+
  theme(panel.background = element_blank(), axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust= 1, size = 8))
#dev.off()
```



#### Generate barplot of cell per cluster per condition
```{r fig.height=5, fig.width=8, warning=FALSE}
# Counting celltypes in timepoints
V<- ChipPatients_filteredStar.combined@meta.data
tmp2<-ChipPatients_filteredStar.combined@meta.data$orig.ident
tmp<-trimws(ChipPatients_filteredStar.combined@meta.data$orig.ident, which = "left", )
orig.ident.ordered<-factor(str_sort(unique(trimws(ChipPatients_filteredStar.combined@meta.data$orig.ident)),numeric = TRUE))

V$orig.ident<-factor(V$orig.ident,levels = orig.ident.ordered)
V$celltypes<-factor(V$celltypes)

Summary.Celltypes <- V %>% count(orig.ident, condition,celltypes,.drop = FALSE) %>% group_by(orig.ident) %>%
  mutate(freq = n /sum(n)) %>% complete(celltypes,fill = list(n=0,freq=0))


tmp<-V %>% count(orig.ident, condition,celltypes,.drop = FALSE) 
Summary.Celltypes$celltypes <- factor(Summary.Celltypes$celltypes)

Summary.Celltypes$orig.ident<-factor(Summary.Celltypes$orig.ident,levels = orig.ident.ordered)
#condition<-c()
tmp<-Summary.Celltypes%>%arrange(condition)
#svg(filename = "/media/ATLAS_NGS_storage/Wesley/AnalysisDavid-2019/Unimputed/CD31+/Barplot-CellsperClusterPerSample.svg",width = 15, height = 10)
ggplot(Summary.Celltypes, aes(x=condition, y= freq, fill= orig.ident))+
  geom_col(position = position_dodge(width=0.9), color = "black")+
  facet_wrap(~celltypes, nrow = 2, scales = "free")+
  scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+
  theme(panel.background = element_blank(), axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust= 1, size = 8))

```


#subset monocytes
```{r}
monocytes<- subset(ChipPatients_filteredStar.combined, idents = "CD14+ Monocytes")

monocytes <- RunPCA(object = monocytes, npcs = 30, verbose = FALSE)
# t-SNE and Clustering
#FirstInMan.combined <- RunUMAP(object = FirstInMan.combined, reduction = "pca", dims = 1:20)
monocytes <- RunTSNE(object = monocytes, reduction = "pca", dims = 1:20)
monocytes <- FindNeighbors(object = monocytes, reduction = "pca", dims = 1:10)
monocytes <- FindClusters(monocytes, resolution = 0.5)

DimPlot(monocytes, split.by = "orig.ident", ncol = 5, pt.size = 0.5)
DimPlot(monocytes, split.by = "condition", ncol = 5, pt.size = 0.5)
DimPlot(monocytes, split.by = "condition", ncol = 5, pt.size = 0.5, group.by = "orig.ident")

VlnPlot(monocytes, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3,pt.size = 0.01)


#### Generate barplot of cell per cluster per condition
# Counting celltypes in timepoints
V<- monocytes@meta.data
tmp2<-monocytes@meta.data$orig.ident
tmp<-trimws(monocytes@meta.data$orig.ident, which = "left", )
orig.ident.ordered<-factor(str_sort(unique(trimws(monocytes@meta.data$orig.ident)),numeric = TRUE))

V$orig.ident<-factor(V$orig.ident,levels = orig.ident.ordered)
V$seurat_clusters<-factor(V$seurat_clusters)

Summary.Celltypes <- V %>% count(orig.ident, condition,seurat_clusters,.drop = FALSE) %>% group_by(orig.ident) %>%
  mutate(freq = n /sum(n)) %>% complete(seurat_clusters,fill = list(n=0,freq=0))


Summary.Celltypes$seurat_clusters <- factor(Summary.Celltypes$seurat_clusters)

Summary.Celltypes$orig.ident<-factor(Summary.Celltypes$orig.ident,levels = orig.ident.ordered)
#condition<-c()
tmp<-Summary.Celltypes%>%arrange(condition)
#svg(filename = "/media/ATLAS_NGS_storage/Wesley/AnalysisDavid-2019/Unimputed/CD31+/Barplot-CellsperClusterPerSample.svg",width = 15, height = 10)
ggplot(Summary.Celltypes, aes(x=condition, y= freq, fill= orig.ident))+
  geom_col(position = position_dodge(width=0.9), color = "black")+
  facet_wrap(~seurat_clusters, nrow = 2, scales = "free")+
  scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+
  theme(panel.background = element_blank(), axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust= 1, size = 8))
```

```{r}
monocytes.markers<-FindAllMarkers(monocytes, assay = "RNA", )

write.csv2(x = monocytes.markers, "/media/Helios_scStorage/Wesley/11275/starSolo/MonocyteMarkers.csv")
VlnPlot(monocytes,features = c("NKG7","GZMA","PRF1","KLRD1","MALAT1", "ETS1"), pt.size = 0, assay = "RNA")
```

#recluster monocyte cluster 5
```{r}
monocytes.5<- subset(monocytes, idents = "5")

monocytes.5 <- RunPCA(object = monocytes.5, npcs = 30, verbose = FALSE)
# t-SNE and Clustering
#FirstInMan.combined <- RunUMAP(object = FirstInMan.combined, reduction = "pca", dims = 1:20)
monocytes.5 <- RunTSNE(object = monocytes.5, reduction = "pca", dims = 1:5)
monocytes.5 <- FindNeighbors(object = monocytes.5, reduction = "umap")
monocytes.5 <- FindClusters(monocytes.5, resolution = 0.5)

monocytes.5 <- RunUMAP(object = monocytes.5, reduction = "pca", dims = 1:5)
monocytes.5 <- FindNeighbors(object = monocytes.5, reduction = "umap", dims = 1:5)
monocytes.5 <- FindClusters(monocytes.5, resolution = 0.5)

DimPlot(monocytes.5, split.by = "orig.ident", ncol = 5, pt.size = 0.5, reduction = "umap")


DimPlot(monocytes.5, split.by = "condition", ncol = 5, pt.size = 0.5, reduction = "umap")
DimPlot(monocytes.5, split.by = "condition", ncol = 5, pt.size = 0.5, group.by = "orig.ident")


```




#subset T-cells
```{r}
tcells<- subset(ChipPatients_filteredStar.combined, idents = "T cells")

tcells <- RunPCA(object = tcells, npcs = 30, verbose = FALSE)
# t-SNE and Clustering
#FirstInMan.combined <- RunUMAP(object = FirstInMan.combined, reduction = "pca", dims = 1:20)
tcells <- RunTSNE(object = tcells, reduction = "pca", dims = 1:20)
tcells <- FindNeighbors(object = tcells, reduction = "pca", dims = 1:10)
tcells <- FindClusters(tcells, resolution = 0.5)

DimPlot(tcells, split.by = "orig.ident", ncol = 5, pt.size = 0.5)
DimPlot(tcells, split.by = "condition", ncol = 5, pt.size = 0.5)
DimPlot(tcells, split.by = "condition", ncol = 5, pt.size = 0.5, group.by = "orig.ident")

VlnPlot(tcells, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3,pt.size = 0.01)


#### Generate barplot of cell per cluster per condition
# Counting celltypes in timepoints
V<- tcells@meta.data
tmp2<-tcells@meta.data$orig.ident
tmp<-trimws(tcells@meta.data$orig.ident, which = "left", )
orig.ident.ordered<-factor(str_sort(unique(trimws(tcells@meta.data$orig.ident)),numeric = TRUE))

V$orig.ident<-factor(V$orig.ident,levels = orig.ident.ordered)
V$seurat_clusters<-factor(V$seurat_clusters)

Summary.Celltypes <- V %>% count(orig.ident, condition,seurat_clusters,.drop = FALSE) %>% group_by(orig.ident) %>%
  mutate(freq = n /sum(n)) %>% complete(seurat_clusters,fill = list(n=0,freq=0))


Summary.Celltypes$seurat_clusters <- factor(Summary.Celltypes$seurat_clusters)

Summary.Celltypes$orig.ident<-factor(Summary.Celltypes$orig.ident,levels = orig.ident.ordered)
#condition<-c()
tmp<-Summary.Celltypes%>%arrange(condition)
#svg(filename = "/media/ATLAS_NGS_storage/Wesley/AnalysisDavid-2019/Unimputed/CD31+/Barplot-CellsperClusterPerSample.svg",width = 15, height = 10)
ggplot(Summary.Celltypes, aes(x=condition, y= freq, fill= orig.ident))+
  geom_col(position = position_dodge(width=0.9), color = "black")+
  facet_wrap(~seurat_clusters, nrow = 2, scales = "free")+
  scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+
  theme(panel.background = element_blank(), axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust= 1, size = 8))

```
