---
title: "First in man study from Patient Cohorts (Seurat3)"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---
  
# 1.) Import packages
```{r message=FALSE}
#load libraries
library(dplyr)
library(ggpubr)
library(reshape2)
require(scales)
library(ggplot2)
library(Seurat)
library(pheatmap)
 
source("/home/david/scRNA-SEQ-ZMM/Import10X-HelperFunctions_SeuratV3.R")
sink(file = "/media/Helios_scStorage/Wesley/103773-001/FirstInMan.rmd.log", append = TRUE, split = TRUE)
```


## 1.2) Define static parameters
```{r}
#Static Parameters 
Paths <- c("/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-001/outs/filtered_feature_bc_matrix",
"/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-002/outs/filtered_feature_bc_matrix",
"/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-003/outs/filtered_feature_bc_matrix",
"/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-004/outs/filtered_feature_bc_matrix",
"/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-005/outs/filtered_feature_bc_matrix",
"/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-006/outs/filtered_feature_bc_matrix",
"/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-007/outs/filtered_feature_bc_matrix",
"/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-008/outs/filtered_feature_bc_matrix",
"/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-009/outs/filtered_feature_bc_matrix",
"/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-010/outs/filtered_feature_bc_matrix",
"/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-011/outs/filtered_feature_bc_matrix",
"/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-012/outs/filtered_feature_bc_matrix",
"/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-013/outs/filtered_feature_bc_matrix",
"/media/Helios_scStorage/Wesley/103773-001/cellranger/103773-001-014/outs/filtered_feature_bc_matrix"
)


Samplenames <- c("Pat127_D1_predose_1.5","Pat127_D4_1.5","Pat128_D1_predose_Placebo",
"Pat128_D4_Placebo","Pat132_D1_predose_1.5","Pat132_D4_1.5",
"Pat130_D1_predose_Placebo","Pat130_D4_Placebo","Pat129_D1_predose_1.5",
"Pat129_D4_1.5","Pat142_D1_predose_1.5","Pat142_D4_1.5",
"Pat137_D1_predose_1.5","Pat137_D4_1.5")
```


## 1.3) import and combine the raw cellranger counts with CCA
```{r}
SeuratObjectList <- list()
for (i in 1:length(Paths)) {
  SeuratObjectList[[i]]<-Importer(pathway = Paths[i],id = Samplenames[i], performNormalisation = TRUE, performVariableGeneDetection = TRUE, FilterCells = TRUE)
}
```

```{r}
for (i in 1:length(SeuratObjectList)) {
  tmpid<-levels(Idents(SeuratObjectList[[i]]))
  print(tmpid)
  
  tmp<-SeuratObjectList[[i]]
  gg <- VlnPlot(object = tmp, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3, group.by = "orig.ident") + ggtitle(tmpid)
  print(gg)
  tmp<-ScaleData(object = tmp)
  tmp<-RunPCA(object = tmp, verbose = FALSE, ndims.print = 0)
  DimHeatmap(object = tmp, dims = 1:10, )
  gg<-ElbowPlot(tmp, ndims = 10) + labs(title=as.character(i))
  print(gg)
}
```

```{r}
FirstInMan.anchors <- FindIntegrationAnchors(object.list = SeuratObjectList, dims = 1:10, k.filter = 20)
FirstInMan.combined <- IntegrateData(anchorset = FirstInMan.anchors, dims = 1:10)
```

```{r}
DefaultAssay(object = FirstInMan.combined) <- "integrated"

# Run the standard workflow for visualization and clustering
FirstInMan.combined <- ScaleData(object = FirstInMan.combined, verbose = FALSE)
FirstInMan.combined <- RunPCA(object = FirstInMan.combined, npcs = 30, verbose = FALSE)
# t-SNE and Clustering
#FirstInMan.combined <- RunUMAP(object = FirstInMan.combined, reduction = "pca", dims = 1:20)
FirstInMan.combined <- RunTSNE(object = FirstInMan.combined, reduction = "pca", dims = 1:20)
FirstInMan.combined <- FindNeighbors(object = FirstInMan.combined, reduction = "pca", dims = 1:20)
FirstInMan.combined <- FindClusters(FirstInMan.combined, resolution = 0.5)
```


```{r }
condition<-c()
for (ident in FirstInMan.combined@meta.data$orig.ident) {
  tmp<-unlist(strsplit(ident,split = "_"))
  currentBarcode<-paste0(tmp[2:length(tmp)],collapse = "_")
  condition<-c(condition,currentBarcode)
}
names(condition)<-names(FirstInMan.combined@active.ident)
FirstInMan.combined$condition<-condition
```

```{r,fig.height=8, fig.width=15 }
DimPlot(object = FirstInMan.combined, label=T, pt.size = 0.1, do.return=TRUE)
DimPlot(object = FirstInMan.combined, group.by = "orig.ident", pt.size = 0.001, split.by = "condition")
DimPlot(object = FirstInMan.combined, group.by = "seurat_clusters", pt.size = 0.001, split.by = "condition")
DimPlot(object = FirstInMan.combined, group.by = "condition", pt.size = 0.001)
FeaturePlot(FirstInMan.combined, features = c("IL7R","CD14","MS4A1","CD8A","NKG7","FCGR3A","FCER1A","PPBP","CD4"), min.cutoff = 0, label = TRUE, label.size = 4)
FeaturePlot(FirstInMan.combined, features = c("IL7R","CD4"), min.cutoff = 0, label = TRUE, label.size = 4)

```
```{r}

```

```{r}
table(FirstInMan.combined$sample)
table(FirstInMan.combined$orig.ident)
table(FirstInMan.combined$condition)
table(FirstInMan.combined$seurat_clusters)
```






#Find Cluster specific Genes
```{r}
Idents(FirstInMan.combined)<-"seurat_clusters" 
FirstInMan.combined.markers<-FindAllMarkers(object = FirstInMan.combined, assay = "RNA", only.pos = TRUE)
TopGenesPerCluster<- FirstInMan.combined.markers %>% group_by(cluster) %>% top_n(2, avg_logFC)
```

```{r}
features<-unique(TopGenesPerCluster$gene)
DotPlot(FirstInMan.combined, features = rev(features), group.by = "seurat_clusters", assay = "RNA", ) + theme(axis.text.x = element_text(angle = 90))

#marker_genes = {'CD4 T cells':{'IL7R'},'CD14+ Monocytes':{'CD14',
#                 'LYZ'}, 'B cells':{'MS4A1'}, 'CD8 T cells':{'CD8A'},
#                 'NK cells':{'GNLY', 'NKG7'}, 'FCGR3A+ Monocytes':
#                 {'FCGR3A', 'MS4A7'}, 'Dendritic Cells':{'FCER1A',
#                 'CST3'}, 'Megakaryocytes':{'PPBP'}}


marker_genes<-c("GNLY","NKG7","IL7R","CD8A","MS4A1","FCGR3A","MS4A7","LYZ","CD14","CST3","FCER1A","PPBP")
DotPlot(FirstInMan.combined, features = rev(marker_genes), group.by = "seurat_clusters", assay = "RNA", ) + theme(axis.text.x = element_text(angle = 90))
```

#Rename Idents
```{r}
Heart.combined <- RenameIdents(Heart.combined, `0` = "Cardiomiocytes", `1` = "Fibroblasts", `2` = "ECs", 
    `3` = "Dentritic Cells", `4` = "Fibroblasts", `5` = "ECs", `6` = "Pericytes", `7` = "Dentritic Cells", `8` = "Fibroblasts", `9` = "ECs", 
    `10` = "Cardiomiocytes", `11` = "Dentritic Cells", `12` = "ECs", `13` = "Fibroblasts/ECs",`14` = "Cardiomiocytes", 
    `15` = "Cardiomiocytes", `16` = "SWL", `17` = "Cardiomiocytes", 
    `18` = "Pericytes/ECs", `19` = "Dentritic Cells", `20` = "Cardiomiocytes/Fibroblasts")


#                     0             1           2           3           4                 5           6               7             8         9     
#clusterNames<-c("NK cells","CD4 T cells","CD8 T cells","CD4 T cells","B cells","FCGR3A+ Monocytes","NK cells","CD4 T cells","CD14+ Monocytes","NK cells",
            #         10           11               12            13            14
#                "NK cells", "Plasma Cells","Dendritic Cells","CD4 T cells","CD4 T cells")
#Idents(FirstInMan.combined)<-"seurat_clusters"
#names(clusterNames) <- levels(FirstInMan.combined)
#FirstInMan.combined <- RenameIdents(FirstInMan.combined, clusterNames)


FirstInMan.combined <- RenameIdents(FirstInMan.combined,'0'="NK cells",'1'="CD4 T cells",'2'="CD8 T cells",'3'="CD4 T cells",
                                                        '4'="B cells",'5'="FCGR3A+ Monocytes",'6'="NK cells",'7'="CD4 T cells",
                                                        '8'="CD14+ Monocytes",'9'="NK cells",'10'="NK cells",'11'= "Plasma Cells",
                                                        '12'="Dendritic Cells",'13'="CD4 T cells",'14'="CD4 T cells")
FirstInMan.combined$celltypes<-Idents(FirstInMan.combined)

```

```{r}
DimPlot(object = FirstInMan.combined, group.by = "celltypes", pt.size = 0.1, label = TRUE, label.size = 6)
DimPlot(object = FirstInMan.combined, group.by = "celltypes",split.by = "condition", pt.size = 0.1, label = TRUE, label.size = 6)

```


#### Generate barplot of cell per cluster per condition
```{r fig.height=5, fig.width=8, warning=FALSE}
# Counting celltypes in timepoints
library(stringr)
library(tidyr)

library(dplyr)
library(ggplot2)
library(scales)
library(Seurat)
V<- FirstInMan.combined@meta.data
condition.ordered<-str_sort(unique(FirstInMan.combined@meta.data$condition),numeric = TRUE)


V$condition<-factor(V$condition,levels = condition.ordered)
V$celltypes<-factor(V$celltypes)

Summary.Celltypes <- V %>% count(condition,celltypes,.drop = FALSE) %>% group_by(condition) %>%
  mutate(freq = n /sum(n)) %>% complete(celltypes,fill = list(n=0,freq=0))

Summary.Celltypes$celltypes <- factor(Summary.Celltypes$celltypes)
condition<-c()

#svg(filename = "/media/ATLAS_NGS_storage/Wesley/AnalysisDavid-2019/Unimputed/CD31+/Barplot-CellsperClusterPerSample.svg",width = 15, height = 10)
ggplot(Summary.Celltypes, aes(x=condition, y= freq, fill= condition))+
  geom_col(width = 0.9, color = "black")+
  facet_wrap(~celltypes, nrow = 2, scales = "free")+
  scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+
  theme(panel.background = element_blank(), axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust= 1, size = 8))
#dev.off()
```



#### Generate barplot of cell per cluster per condition
```{r fig.height=5, fig.width=8, warning=FALSE}
# Counting celltypes in timepoints
V<- FirstInMan.combined@meta.data
tmp2<-FirstInMan.combined@meta.data$orig.ident
tmp<-trimws(FirstInMan.combined@meta.data$orig.ident, which = "left", )
orig.ident.ordered<-factor(str_sort(unique(trimws(FirstInMan.combined@meta.data$orig.ident)),numeric = TRUE))

V$orig.ident<-factor(V$orig.ident,levels = orig.ident.ordered)
V$celltypes<-factor(V$celltypes)

Summary.Celltypes <- V %>% count(orig.ident, condition,celltypes,.drop = FALSE) %>% group_by(condition) %>%
  mutate(freq = n /sum(n)) %>% complete(celltypes,fill = list(n=0,freq=0))


tmp<-V %>% count(orig.ident, condition,celltypes,.drop = FALSE) 
Summary.Celltypes$celltypes <- factor(Summary.Celltypes$celltypes)

Summary.Celltypes$orig.ident<-factor(Summary.Celltypes$orig.ident,levels = orig.ident.ordered)
#condition<-c()
tmp<-Summary.Celltypes%>%arrange(condition)
#svg(filename = "/media/ATLAS_NGS_storage/Wesley/AnalysisDavid-2019/Unimputed/CD31+/Barplot-CellsperClusterPerSample.svg",width = 15, height = 10)
ggplot(Summary.Celltypes, aes(x=condition, y= freq, fill= orig.ident))+
  geom_col(width = 0.9, color = "black")+
  facet_wrap(~celltypes, nrow = 2, scales = "free")+
  scale_y_continuous(name = "Percent per timepoint", labels = scales::percent_format())+
  theme(panel.background = element_blank(), axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust= 1, size = 8))

```


# Find DEG after Treatment
```{r}
table(FirstInMan.combined$condition)
Idents(FirstInMan.combined) <- "condition"
DEG_D1Placebo_vs_D4_Placebo <- FindMarkers(object = FirstInMan.combined, ident.1 = "D1_predose_Placebo", ident.2 = "D4_Placebo", assay = "RNA", slot = "data", logfc.threshold="0.1", test.use = "bimod",)
DEG_D1Predose_1.5_vs_D4_1.5 <- FindMarkers(object = FirstInMan.combined, ident.1 = "D1_predose_1.5", ident.2 = "D4_1.5", assay = "RNA", slot = "data", logfc.threshold="0.1", test.use = "bimod")

DEG_D1Placebo_vs_D4_Placebo$Gene<-rownames(DEG_D1Placebo_vs_D4_Placebo)
DEG_D1Predose_1.5_vs_D4_1.5$Gene<-rownames(DEG_D1Predose_1.5_vs_D4_1.5)

set1<-DEG_D1Placebo_vs_D4_Placebo[DEG_D1Placebo_vs_D4_Placebo$p_val<0.05,]
set2<-DEG_D1Predose_1.5_vs_D4_1.5[DEG_D1Predose_1.5_vs_D4_1.5$p_val<0.05,]
write.csv2(set1, file = "/media/Helios_scStorage/Wesley/103773-001/cellranger/Seurat3_Analysis_David/DEG_D1Placebo_vs_D4_Placebo.csv")
write.csv2(set2, file = "/media/Helios_scStorage/Wesley/103773-001/cellranger/Seurat3_Analysis_David/DEG_D1Predose_1.5_vs_D4_1.5.csv")


```

```{r}
save.image("/media/Helios_scStorage/Wesley/103773-001/Workspace_12.11.19.R.RData")
load("/media/Helios_scStorage/Wesley/103773-001/Workspace_12.11.19.R.RData")
```


# Check miR-92A targets
```{r}
hsa_miR_92a_1_5p = read.csv2("/media/Helios_scStorage/Wesley/103773-001/cellranger/Seurat3_Analysis_David/hsa-miR-92a-1-5p.csv", sep = ",", header = T)
hsa_miR_92a_2_5p = read.csv2("/media/Helios_scStorage/Wesley/103773-001/cellranger/Seurat3_Analysis_David/hsa-miR-92a-2-5p.csv", sep = ",", header = T)
hsa_miR_92a_3p = read.csv2("/media/Helios_scStorage/Wesley/103773-001/cellranger/Seurat3_Analysis_David/hsa-miR-92a-3p.csv", sep = ",", header = T)


fet<-c(as.character(hsa_miR_92a_1_5p$Gene.Symbol[0:30]))
levels(FirstInMan.combined)
levels(FirstInMan.combined)<-c("Pat128_D1_predose_Placebo","Pat130_D1_predose_Placebo",
                                "Pat128_D4_Placebo","Pat130_D4_Placebo",
                                "Pat127_D1_predose_1.5","Pat129_D1_predose_1.5","Pat132_D1_predose_1.5","Pat142_D1_predose_1.5","Pat137_D1_predose_1.5",
                                "Pat127_D4_1.5","Pat129_D4_1.5", "Pat132_D4_1.5", "Pat142_D4_1.5","Pat137_D4_1.5")
Idents(FirstInMan.combined)<-"orig.ident"
fet<-c(as.character(hsa_miR_92a_1_5p$Gene.Symbol))

########################################################################################################
#i all patients studied accept 132 and 142
FirstInMan.combined_i<-subset(FirstInMan.combined, idents = c("Pat128_D1_predose_Placebo","Pat130_D1_predose_Placebo",
                                "Pat128_D4_Placebo","Pat130_D4_Placebo",
                                "Pat127_D1_predose_1.5","Pat129_D1_predose_1.5","Pat137_D1_predose_1.5",
                                "Pat127_D4_1.5","Pat129_D4_1.5","Pat137_D4_1.5") )

Idents(FirstInMan.combined_i)<-"orig.ident"
levels(FirstInMan.combined_i)<-c("Pat128_D1_predose_Placebo","Pat130_D1_predose_Placebo",
                                "Pat128_D4_Placebo","Pat130_D4_Placebo",
                                "Pat127_D1_predose_1.5","Pat129_D1_predose_1.5","Pat137_D1_predose_1.5",
                                "Pat127_D4_1.5","Pat129_D4_1.5","Pat137_D4_1.5")


table(FirstInMan.combined_i$orig.ident)
DoHeatmap(FirstInMan.combined_i, features = hsa_miR_92a_3p$Gene.Symbol[1:100], assay = "RNA", slot = 'data', disp.min = 1  , disp.max = 3, size = 2, ) + NoLegend()

DoHeatmap(FirstInMan.combined, features = fet, assay = "RNA", slot = 'data')


#NK Cells
Idents(FirstInMan.combined_i)<-"celltypes"
FirstInMan.combined_i_nkCells<-subset(FirstInMan.combined_i, idents = c("NK cells") )
Idents(FirstInMan.combined_i_nkCells)<-"orig.ident"
levels(FirstInMan.combined_i_nkCells)<-c("Pat128_D1_predose_Placebo","Pat130_D1_predose_Placebo",
                                "Pat128_D4_Placebo","Pat130_D4_Placebo",
                                "Pat127_D1_predose_1.5","Pat129_D1_predose_1.5","Pat137_D1_predose_1.5",
                                "Pat127_D4_1.5","Pat129_D4_1.5","Pat137_D4_1.5")
DoHeatmap(FirstInMan.combined_i_nkCells, features = hsa_miR_92a_3p$Gene.Symbol[1:100], assay = "RNA", slot = 'data', disp.min = 1  , disp.max = 3, size = 2, ) + NoLegend()

#CD8
Idents(FirstInMan.combined_i)<-"celltypes"
FirstInMan.combined_i_cd8<-subset(FirstInMan.combined_i, idents = c("CD8 T cells") )
Idents(FirstInMan.combined_i_cd8)<-"orig.ident"
levels(FirstInMan.combined_i_cd8)<-c("Pat128_D1_predose_Placebo","Pat130_D1_predose_Placebo",
                                "Pat128_D4_Placebo","Pat130_D4_Placebo",
                                "Pat127_D1_predose_1.5","Pat129_D1_predose_1.5","Pat137_D1_predose_1.5",
                                "Pat127_D4_1.5","Pat129_D4_1.5","Pat137_D4_1.5")
DoHeatmap(FirstInMan.combined_i_cd8, features = hsa_miR_92a_3p$Gene.Symbol[1:100], assay = "RNA", slot = 'data', disp.min = 1  , disp.max = 3, size = 2, ) + NoLegend()

#CD4
Idents(FirstInMan.combined_i)<-"celltypes"
FirstInMan.combined_i_cd4<-subset(FirstInMan.combined_i, idents = c("CD4 T cells") )
Idents(FirstInMan.combined_i_cd4)<-"orig.ident"
levels(FirstInMan.combined_i_cd4)<-c("Pat128_D1_predose_Placebo","Pat130_D1_predose_Placebo",
                                "Pat128_D4_Placebo","Pat130_D4_Placebo",
                                "Pat127_D1_predose_1.5","Pat129_D1_predose_1.5","Pat137_D1_predose_1.5",
                                "Pat127_D4_1.5","Pat129_D4_1.5","Pat137_D4_1.5")
DoHeatmap(FirstInMan.combined_i_cd4, features = hsa_miR_92a_3p$Gene.Symbol[1:100], assay = "RNA", slot = 'data', disp.min = 1  , disp.max = 3, size = 2, ) + NoLegend()

#averaged
FirstInMan.combined_i_cd4_averaged<-AverageExpression(object = FirstInMan.combined_i_cd4)
tmp<-intersect(hsa_miR_92a_3p$Gene.Symbol, rownames(FirstInMan.combined_i_cd4_averaged[[1]]))
library(pheatmap)
pheatmap(FirstInMan.combined_i_cd4_averaged[[1]][tmp[1:100],], cluster_rows = FALSE)
########################################################################################################
#ii only two patients studied
FirstInMan.combined_ii<-subset(FirstInMan.combined, idents = c("Pat130_D1_predose_Placebo","Pat130_D4_Placebo",
                                                              "Pat129_D1_predose_1.5","Pat129_D4_1.5") )
Idents(FirstInMan.combined_ii)<-"orig.ident"
levels(FirstInMan.combined_ii)<-c("Pat130_D1_predose_Placebo","Pat130_D4_Placebo",
                                  "Pat129_D1_predose_1.5","Pat129_D4_1.5")


table(FirstInMan.combined_i$orig.ident)
DoHeatmap(FirstInMan.combined_ii, features = hsa_miR_92a_3p$Gene.Symbol[1:100], assay = "RNA", slot = 'data', disp.min = 1  , disp.max = 3, size = 2, ) + NoLegend()


FirstInMan.combined_ii_averaged<-AverageExpression(object = FirstInMan.combined_ii)
#remove all 0 values
FirstInMan.combined_ii_averaged_RNA<-FirstInMan.combined_ii_averaged[[1]][rowSums(abs(FirstInMan.combined_ii_averaged[[1]])) > 2,]
tmp<-intersect(hsa_miR_92a_3p$Gene.Symbol, rownames(FirstInMan.combined_ii_averaged_RNA))

pheatmap(FirstInMan.combined_ii_averaged_RNA[tmp,], cluster_cols = FALSE)


table(FirstInMan.combined$orig.ident)
DoHeatmap(FirstInMan.combined, features = fet, group.by = "orig.ident", assay = "RNA", slot = 'data')

DoHeatmap(FirstInMan.combined, features = fet, assay = "RNA", slot = 'data')
```


```{r}

union.targets.Placebo<-intersect(DEG_D1Placebo_vs_D4_Placebo$Gene,mir92a.table$Gene.Symbol)
union.targets.Treatment<-intersect(DEG_D1Predose_1.5_vs_D4_1.5$Gene,mir92a.table$Gene.Symbol)

head(mir92a.table$Gene.Symbol)

VlnPlot(object = FirstInMan.combined, features = mir92a.table$Gene.Symbol[1:9])

```



```{r}
DefaultAssay(FirstInMan.combined)<-"RNA"
tmp<-ScaleData(FirstInMan.combined)
VlnPlot(FirstInMan.combined, features = "CD14","PECAM1")
```


#regulation of top 50 mir92A targets
```{r}
mir92Targets<-intersect(mir92a.table[0:500,]$Gene.Symbol,rownames(FirstInMan.combined@assays$RNA))

patients <- c("Pat127_D1_predose_1.5","Pat127_D4_1.5",
              "Pat129_D1_predose_1.5","Pat129_D4_1.5",
              "Pat132_D1_predose_1.5","Pat132_D4_1.5",
              "Pat137_D1_predose_1.5","Pat137_D4_1.5",
              "Pat142_D1_predose_1.5","Pat142_D4_1.5",
              "Pat128_D1_predose_Placebo","Pat128_D4_Placebo",
              "Pat130_D1_predose_Placebo","Pat130_D4_Placebo")
Idents(FirstInMan.combined) <- "orig.ident"
Idents(FirstInMan.combined) <- "celltypes"

celltypes<-levels(FirstInMan.combined$celltypes)
celltype<-celltypes[1]
for (celltype in celltypes) {
  df<-data.frame(Gene=mir92Targets)

  tmpSeurat<-subset(FirstInMan.combined, idents = celltype)
  Idents(tmpSeurat) <- "orig.ident"

  avg<-AverageExpression(tmpSeurat, assays = "RNA", features = mir92Targets, verbose = FALSE)
  avg$RNA<-exp(avg$RNA)
  if (length(avg$RNA)==length(unique(FirstInMan.combined$orig.ident))) {
      df$Tre_127_FC<-avg$RNA$Pat127_D4_1.5/avg$RNA$Pat127_D1_predose_1.5
    df$Tre_129_FC<-avg$RNA$Pat129_D4_1.5/avg$RNA$Pat129_D1_predose_1.5
    df$Tre_132_FC<-avg$RNA$Pat132_D4_1.5/avg$RNA$Pat132_D1_predose_1.5
    df$Tre_137_FC<-avg$RNA$Pat137_D4_1.5/avg$RNA$Pat137_D1_predose_1.5
    df$Tre_142_FC<-avg$RNA$Pat142_D4_1.5/avg$RNA$Pat142_D1_predose_1.5
    df$Pla_128_FC<-avg$RNA$Pat128_D4_Placebo/avg$RNA$Pat128_D1_predose_Placebo
    df$Pla_130_FC<-avg$RNA$Pat130_D4_Placebo/avg$RNA$Pat130_D1_predose_Placebo
    
    df_melted<-melt(df)
    gg <- ggplot(df_melted, aes(x=variable, y=value)) + 
      geom_boxplot() + scale_y_continuous(limits = c(0,2)) + 
      labs(title = celltype)
    print(gg)
  }
  else  {
    cat("Skipping ",celltype, "because not enough cells")
  }
  
}
tail(FirstInMan.combined@assays$RNA)
#loop over celltypes

#loop over patient
VlnPlot(FirstInMan.combined,features = c("GLRA1"))

```


#ext6rect upregulated mir92Atargets
```{r}
mir92Targets<-intersect(mir92a.table[0:500,]$Gene.Symbol,rownames(FirstInMan.combined@assays$RNA))

patients <- c("Pat127_D1_predose_1.5","Pat127_D4_1.5",
              "Pat129_D1_predose_1.5","Pat129_D4_1.5",
              "Pat132_D1_predose_1.5","Pat132_D4_1.5",
              "Pat137_D1_predose_1.5","Pat137_D4_1.5",
              "Pat142_D1_predose_1.5","Pat142_D4_1.5",
              "Pat128_D1_predose_Placebo","Pat128_D4_Placebo",
              "Pat130_D1_predose_Placebo","Pat130_D4_Placebo")
Idents(FirstInMan.combined) <- "orig.ident"
Idents(FirstInMan.combined) <- "celltypes"


celltypes<-levels(FirstInMan.combined$celltypes)
celltype<-celltypes[1]
for (celltype in celltypes) {
  df<-data.frame(Gene=mir92Targets)

  tmpSeurat<-subset(FirstInMan.combined, idents = celltype)
  Idents(tmpSeurat) <- "orig.ident"

  avg<-AverageExpression(tmpSeurat, assays = "RNA", features = mir92Targets, verbose = FALSE)
  avg$RNA<-exp(avg$RNA)
  if (length(avg$RNA)==length(unique(FirstInMan.combined$orig.ident))) {
      df$Tre_127_FC<-avg$RNA$Pat127_D4_1.5/avg$RNA$Pat127_D1_predose_1.5
    df$Tre_129_FC<-avg$RNA$Pat129_D4_1.5/avg$RNA$Pat129_D1_predose_1.5
    df$Tre_132_FC<-avg$RNA$Pat132_D4_1.5/avg$RNA$Pat132_D1_predose_1.5
    df$Tre_137_FC<-avg$RNA$Pat137_D4_1.5/avg$RNA$Pat137_D1_predose_1.5
    df$Tre_142_FC<-avg$RNA$Pat142_D4_1.5/avg$RNA$Pat142_D1_predose_1.5
    df$Pla_128_FC<-avg$RNA$Pat128_D4_Placebo/avg$RNA$Pat128_D1_predose_Placebo
    df$Pla_130_FC<-avg$RNA$Pat130_D4_Placebo/avg$RNA$Pat130_D1_predose_Placebo
    write.csv(x = df, file = paste0("/media/Helios_scStorage/Wesley/103773-001/cellranger/Seurat3_Analysis_David/CelltypeSpecificMir92ATargets/",celltype,".csv"))
    
  }
  else  {
    cat("Skipping ",celltype, "because not enough cells")
  }
  
}
#tail(FirstInMan.combined@assays$RNA)
#loop over celltypes

#loop over patient
#VlnPlot(FirstInMan.combined,features = c("GLRA1"))

```

Generate Seurat object for Patient 129 and 130
```{r}

Idents(FirstInMan.combined) <- "orig.ident"
table(Idents(FirstInMan.combined))
Pat129<-subset(FirstInMan.combined, idents = c("Pat129_D1_predose_1.5","Pat129_D4_1.5"))
FeaturePlot(Pat129, features = c("CD14", "CD3E"), min.cutoff = 0, max.cutoff = 1, split.by = "ident")
VlnPlot(Pat129, features = c("CD14", "CD3E"))


Idents(object = FirstInMan.combined)

```

